---
title: "Relation between Moments across Datasets"
subtitle: ""
author: "Lucia Campese"
date: "Apr 2020"
output:
  html_document:
    code_folding: hide
    self_contained: true
---

```{r import, include=F}
knitr::opts_chunk$set(message = F, error = F, warning = F, echo = F,
                          cache = T)
```

<style>
.column-left{
  float: left;
  width: 50%;
  text-align: left;
}
.column-right{
  float: right;
  width: 50%;
  text-align: right;
}
</style>

<br>

### Aim 

We want to find the theoretical distributions that better fit our data; to do that, we study the relation between the moments of our distributions (mean and variance, skewness and kurtosis).

<br>

### Datasets
#### metaB: 
V9 region; OTU relative abundances; Diatoms; 20-180, SUR. File: barv2016202_swarm_d1_t100.

#### metaG: 
MATOU-v2 unigene relative abundances (RPKM normalization) renormalized on diatoms total abundance per station; Diatoms; 20-180; SUR

#### metaT: 
MATOU-v2 unigene relative abundances (RPKM normalization) renormalized on diatoms total abundance per station; Diatoms; 20-180; SUR

#### Transcriptomics P.multistriata: 
Transcriptomes of P. multistriata (Basu et al, 2017); normalization CPM (Counts Per Million) 

<br>



Feature    | metaB                | metaG             | metaT              | Transcriptome
---------- | -------------------- | ----------------- |------------------- | ----------------
unit       | OTU                  | unigene           | trascribed unigene | transcribed gene
condition  | sampling station     | sampling station  | sampling station   | cell
value type | rel.ab (sum per st=1)| rel.ab (RPKM+dia) | rel.ab(RPKM+dia)   | CPM


<br>

<br>

## A) Community level: Relation between variables (columns)

How can we address whether the variability we observe between sampling stations is due to a real biological signal or to background noise/technical biases?



### 1. Richness{.tabset}

#### metaB

```{r a1}
library(tidyverse)
library(data.table)
library(e1071)
library(readxl)

#### metaB barv2016202_swarm_d1_t100.txt <- swarm di Greta

#metab
metab <- fread("C:/Users/Userszn/Documents/PhD/TARA_Data/metaB/diatoms/barv2016202_swarm_d1_t100.txt", 
               sep = " ", stringsAsFactors = F)


metab1 <- metab %>% 
  rename(OTU = V1) %>% 
  pivot_longer(`TARA_158_SRF_20-180`:`TARA_078_DCM_20-180`) %>% 
  filter(grepl("SRF", name), value >0) %>% 
  separate(name, into = c("TARA", "St.label", "roba", "roba2"), sep = "_") %>% 
  select(OTU, St.label, value)

metabrelab <- metab1 %>% 
  group_by(St.label) %>% 
  mutate(relab = value/sum(value)) %>% 
  ungroup


metab_richness <- metabrelab %>% 
  group_by(St.label) %>% 
  summarise(n_otus = n_distinct(OTU)) %>% 
  ungroup

metab_richness_table <-metab_richness %>% 
  select(n_otus) %>% 
  rename("n of OTUs" = n_otus) %>% 
  summary()

metab_richness %>% 
  ggplot() +
  aes(x = n_otus) +
  geom_histogram(aes(y = ..density..),
                 bins = 100, 
                 color = "grey30", 
                 fill = "white") +
  geom_density(alpha = .2, fill = "antiquewhite3") +
  xlab("n of OTUs") +
  #scale_x_continuous(breaks=unique(metab_ubiquity$ubiquity)) +
  theme_bw() +
  ggtitle(paste0("Station richness; ", n_distinct(metab_richness$St.label), " stations"),
          subtitle = "metaB, Diatoms; 20-180um, SUR") +
  annotation_custom(gridExtra::tableGrob(metab_richness_table), xmin=400, xmax=500, 
                    ymin=0.002, ymax=0.004)
```


```{r eval=FALSE}
library(tidyverse)
library(data.table)
library(e1071)
library(readxl)

#### metaB data drom N.Henry/F.Ibalbarz


metab.tot <- fread("C:/Users/Userszn/Documents/PhD/TARA_Data/metaB/all_taxa/globaldataset.otus.v20171106.withfunctions", sep = "\t", stringsAsFactors = F)

metab.dia <- metab.tot %>% 
  filter(grepl("Bacillariophyta", lineage))

env <- fread("C:/Users/Userszn/Documents/PhD/TARA_Data/metab-env.from.N.Henry.byFederico/TARA_CONTEXT_95_SEQ_STATIONS_V9_v2.txt")

env.20180sur <- env[,-22] %>% 
  filter(Depth == "SRF",
         Fraction.size == "20-180") %>% 
  rename(St.label = Station.label) %>% 
  select(Sample.id, St.label)

metab.dia1 <- metab.dia %>% 
  pivot_longer(BV9_1:TV9_99) %>% 
  rename(OTU = cid, Sample.id = name) %>% 
  select(OTU, Sample.id, value) %>% 
  filter(value > 0)

metab.dia.final <- metab.dia1 %>% 
  inner_join(env.20180sur, by = "Sample.id") %>% 
  select(OTU, St.label, value)

metabrelab <- metab.dia.final %>% 
  group_by(St.label) %>% 
  mutate(relab = value/sum(value)) %>% 
  ungroup


save(metabrelab, file = "C:/Users/Userszn/Documents/PhD/TARA_Data/metab-env.from.N.Henry.byFederico/metabrelab.RData")
```


```{r eval=FALSE}

load("C:/Users/Userszn/Documents/PhD/TARA_Data/metab-env.from.N.Henry.byFederico/metabrelab.RData")
metab_richness <- metabrelab %>% 
  group_by(St.label) %>% 
  summarise(n_otus = n_distinct(OTU))

metab_richness_table <-metab_richness %>% 
  select(n_otus) %>% 
  rename("n of OTUs" = n_otus) %>% 
  summary()

metab_richness %>% 
  ggplot() +
  aes(x = n_otus) +
  geom_histogram(aes(y = ..density..),
                 bins = 100, 
                 color = "grey30", 
                 fill = "white") +
  geom_density(alpha = .2, fill = "antiquewhite3") +
  xlab("n of OTUs") +
  theme_bw() +
  ggtitle(paste0("Station richness; ", n_distinct(metab_richness$St.label), " stations"),
          subtitle = "metaB, Diatoms; 20-180um, SUR") +
  annotation_custom(gridExtra::tableGrob(metab_richness_table), xmin=500, xmax=700, 
                    ymin=0.002, ymax=0.004)
```


#### metaG

```{r a2}
metag <- fread("C:/Users/Userszn/Documents/PhD/TARA_Data/metaG/diatoms/metaG_diatoms_QQSS_SUR_norm_v2.ssv", sep = ",", header = F) %>%
  separate(V2, into = c("value", "St.label"), sep = "\\s") %>% 
  rename(geneid = V1) %>% 
  mutate(St.label = sprintf("%03d",as.numeric(St.label)),
         value = as.numeric(value),
         geneid = as.character(geneid))

metag_richness <- metag %>% 
  group_by(St.label) %>% 
  summarise(n_genes = n_distinct(geneid)) %>% 
  ungroup()


metag_richness_table <-metag_richness %>% 
  select(n_genes) %>% 
  summary()

metag_richness %>% 
  ggplot() +
  aes(x = n_genes) +
  geom_histogram(aes(y = ..density..),
                 bins = 100, 
                 color = "grey30", 
                 fill = "white") +
  geom_density(alpha = .2, fill = "antiquewhite3") +
  xlab("n of unigenes") +
  theme_bw() +
  ggtitle(paste0("Station richness; ", n_distinct(metag_richness$St.label), " stations"),
          subtitle = "metaG, Diatoms; 20-180um, SUR") +
  annotation_custom(gridExtra::tableGrob(metag_richness_table), xmin=2e+05, xmax=3e+05, 
                    ymin=1e-05, ymax=2.5e-05)

```

#### metaT 

```{r a3}
metat <- fread("C:/Users/Userszn/Documents/PhD/TARA_Data/metaT/diatoms/metaT_diatoms_QQSS_SUR_norm_v2.ssv", sep = ",", header = F) %>% 
  separate(V2, into = c("value", "St.label"), sep = "\\s") %>% 
  rename(geneid = V1) %>% 
  mutate(St.label = sprintf("%03d",as.numeric(St.label)),
         value = as.numeric(value),
         geneid = as.character(geneid))

metat_richness <- metat %>% 
  group_by(St.label) %>% 
  summarise(n_genes = n_distinct(geneid)) %>% 
  ungroup()


metat_richness_table <-metat_richness %>% 
  select(n_genes) %>% 
  summary()


metat_richness %>% 
  ggplot() +
  aes(x = n_genes) +
  geom_histogram(aes(y = ..density..),
                 bins = 100, 
                 color = "grey30", 
                 fill = "white") +
  geom_density(alpha = .2, fill = "antiquewhite3") +
  xlab("n of unigenes") +
  theme_bw() +
  ggtitle(paste0("Station richness; ", n_distinct(metat_richness$St.label), " stations"),
          subtitle = "metaT, Diatoms; 20-180um, SUR") +
  annotation_custom(gridExtra::tableGrob(metat_richness_table), xmin=3e+05, xmax=4e+05, 
                    ymin=4e-06, ymax=1e-05)
```


#### P.mu
```{r a4}

#transcriptomics
p.mu_ts <-read_xlsx("C:/Users/Userszn/Documents/PhD/script/Pseudonitzschia/Transcriptomics/Copy of all.annot.xlsx")

p.mu_ts1 <- na.omit(p.mu_ts)

p.mu_ts_richness <- p.mu_ts1 %>% 
  pivot_longer(M2.4_CE:F50b_SL) %>% 
  group_by(name) %>% 
  summarise(n_genes = n_distinct(Row.names)) %>% 
  ungroup()


p.mu_ts_richness_table <- p.mu_ts_richness %>% 
  select(n_genes) %>% 
  summary()

p.mu_ts_richness %>% 
  ggplot() +
  aes(x = n_genes) +
  geom_histogram(aes(y = ..density..),
                 bins = 100, 
                 color = "grey30", 
                 fill = "white") +
  geom_density(alpha = .2, fill = "antiquewhite3") +
  xlab("n of genes") +
  theme_bw() +
  ggtitle(paste0("Condition richness; ", n_distinct(p.mu_ts_richness$name), " conditions?"),
          subtitle = "P. multistriata")  #+
  #nnotation_custom(gridExtra::tableGrob(metag_richness_table), xmin=2e+05, xmax=3e+05, 
            #        ymin=1e-05, ymax=2.5e-05)

```


### 2. RAD{.tabset}

#### metaB

```{r b1}
metabrelab %>% 
  group_by(St.label) %>% 
  mutate(richness = n_distinct(OTU)) %>%
  arrange(desc(relab)) %>%
  mutate(Rank = seq_len(n()),
         `log10 of % relative abundance` = log10(relab)) %>%
  ungroup() %>% 
  ggplot() +
  aes(x = Rank, y = `log10 of % relative abundance`,
      col = richness, group = St.label) +
  geom_line(lwd = 0.5, alpha = 0.25) +
  theme_bw() +
  ggtitle("Whittaker (RAD) on diatom OTUs",
          subtitle = "metaB, 20-180, SUR")


```

#### metaG

```{r b2}
metag %>%
  group_by(St.label) %>%
  mutate(richness = n_distinct(geneid)) %>%
  arrange(desc(value)) %>%
  mutate(Rank = seq_len(n()),
         `log10 of % relative abundance` = log10(value)) %>%
  ggplot() +
  aes(x = Rank, y = `log10 of % relative abundance`,
      col = richness, group = St.label) +
  geom_line(lwd = 0.5, alpha = 0.25) +
  theme_bw() +
  ggtitle("Whittaker (RAD) on diatom unigenes",
          subtitle = "metaG, 20-180, SUR")

```

#### metaT 

```{r b3}
metat %>%
  group_by(St.label) %>%
  mutate(richness = n_distinct(geneid)) %>%
  arrange(desc(value)) %>%
  mutate(Rank = seq_len(n()),
         `log10 of % relative abundance` = log10(value)) %>%
  ggplot() +
  aes(x = Rank, y = `log10 of % relative abundance`,
      col = richness, group = St.label) +
  geom_line(lwd = 0.5, alpha = 0.25) +
  theme_bw() +
  ggtitle("Whittaker (RAD) on diatom unigenes",
          subtitle = "metaT, 20-180, SUR")
```

#### P.multistriata 

```{r b4}
p.mu_ts1 %>% 
  pivot_longer(M2.4_CE:F50b_SL) %>% 
  group_by(name) %>%
  mutate(richness = n_distinct(Row.names)) %>%
  arrange(desc(value)) %>%
  mutate(Rank = seq_len(n()),
         `log10 of % relative abundance` = log10(value)) %>%
  ggplot() +
  aes(x = Rank, y = `log10 of % relative abundance`,
      col = richness, group = name) +
  geom_line(lwd = 0.5, alpha = 0.25) +
  theme_bw() +
  ggtitle("Whittaker (RAD) on P.multistriata transcriptomes",
          subtitle = "20-180, SUR")
```

### 3. Relation between moments : mean-variance{.tabset}

#### metaB

```{r c1}
moments_metab_stations <- metabrelab %>% 
  group_by(St.label) %>%
  summarise(mean = mean(relab),
            median = median(relab),
            variance = var(relab),
            IQR = IQR(relab),
            skewness = skewness(relab),
            kurtosis = kurtosis(relab),
            richness = n_distinct(OTU)) %>%
  mutate(logme = log10(mean), logvar = log10(variance),
         source = c("metab_tara"))

moments_metab_stations %>%
  ggplot() + 
  aes(x=mean, y=variance) + 
  geom_point(aes(col = richness), size = 3) +
  scale_colour_viridis_c() + 
  geom_smooth(method = "lm", formula = y ~ x) +
  ggpubr::stat_regline_equation(label.x.npc = "left", label.y.npc = "top") +
  ggpubr::stat_cor(label.x.npc = "middle", label.y.npc = "bottom") +
  theme_bw() +
  scale_x_log10() +
  scale_y_log10() +
  ggtitle(paste0("Mean and Variance; ",
                 n_distinct(moments_metab_stations$St.label), " stations"),
          subtitle = ("metaB, diatoms, 20-180, SUR")) +
    labs(caption = "log-log")

```

#### metaG

```{r c2}
#load("moments_metag_stations.RData")

moments_metag_stations <- metag %>%
  group_by(St.label) %>%
  summarise(mean = mean(value),
            median = median(value),
            variance = var(value),
            IQR = IQR(value),
            skewness = skewness(value),
            kurtosis = kurtosis(value),
            richness = n_distinct(geneid)) %>%
  mutate(logme = log10(mean), logvar = log10(variance),
         source = c("metag_tara"))


moments_metag_stations %>%
  ggplot() + 
  aes(x=mean, y=variance) + 
  #geom_point(col = "gray", size = 1) +
  geom_point(aes(col=richness), size = 3) +
  scale_colour_viridis_c() +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggpubr::stat_regline_equation(label.x.npc = "left", label.y.npc = "top") +
  ggpubr::stat_cor(label.x.npc = "middle", label.y.npc = "bottom") +
  theme_bw() +
  scale_x_log10() +
  scale_y_log10() +
  ggtitle(paste0("Mean and Variance; ",
                 n_distinct(moments_metag_stations$St.label), " stations"),
          subtitle = ("metaG, diatoms, 20-180, SUR")) +
    labs(caption = "log-log")
```


#### metaT

```{r c3}

moments_metat_stations <- metat %>%
  group_by(St.label) %>%
  summarise(mean = mean(value),
            median = median(value),
            variance = var(value),
            IQR = IQR(value),
            skewness = skewness(value),
            kurtosis = kurtosis(value),
            richness = n_distinct(geneid)) %>%
  mutate(logme = log10(mean), logvar = log10(variance),
         source = c("metat_tara"))


moments_metat_stations %>%
  ggplot() + 
  aes(x=mean, y=variance) + 
  geom_point(aes(col=richness), size=3) +
  scale_color_viridis_c() +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggpubr::stat_regline_equation(label.x.npc = "left", label.y.npc = "top") +
  ggpubr::stat_cor(label.x.npc = "middle", label.y.npc = "bottom") +
  theme_bw() +
  scale_x_log10() +
  scale_y_log10() +
  ggtitle(paste0("Mean and Variance; ",
                 n_distinct(moments_metat_stations$St.label), " stations"),
          subtitle = ("metaT, diatoms, 20-180, SUR")) +
    labs(caption = "log-log")
```

#### P.multistriata

```{r c4}

moments_p.mu_conditions <- p.mu_ts1 %>%
  pivot_longer(M2.4_CE:F50b_SL) %>%
  group_by(name) %>%
  summarise(mean = mean(value),
            median = median(value),
            variance = var(value),
            IQR = IQR(value),
            skewness = skewness(value),
            kurtosis = kurtosis(value),
            richness = n_distinct(Row.names)) %>%
  mutate(logme = log10(mean), logvar = log10(variance),
         source = c("p.mu"))


moments_p.mu_conditions %>%
  ggplot() + 
  aes(x=mean, y=variance) + 
  #geom_point(col = "gray", size = 1) +
  geom_point(aes(col=richness), size=3) +
  scale_color_viridis_c() +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggpubr::stat_regline_equation(label.x.npc = "left", label.y.npc = "top") +
  ggpubr::stat_cor(label.x.npc = "middle", label.y.npc = "bottom") +
  theme_bw() +
  scale_x_log10() +
  scale_y_log10() +
  ggtitle(paste0("Mean and Variance; ",
                 n_distinct(moments_p.mu_conditions$name), " conditions"),
          subtitle = ("P.multistriata transcriptomes")) +
    labs(caption = "log-log")
```

#### all (TARA)

```{r c5}
moments_metaBrelGT_stations <- rbind(moments_metab_stations,
      moments_metag_stations,
      moments_metat_stations)


#moments_between_data <- moments_metaBrelGT_stations %>%
#  group_by(St.label) %>% 
#  mutate( datashared = n_distinct(source)) %>% 
#  ungroup() %>% 
#  filter(datashared == 3) %>% 
#  select(St.label, richness, mean, 
#         median, variance, IQR, source) %>% 
#  pivot_longer(richness:IQR) %>% 
#  select(St.label, name, value, source) %>% 
#  group_by(name) %>% 
#  nest() %>% 
#  ungroup %>% 
#  mutate(roba = map(data, ~spread(.x, source,value)))
##metaB vs metaG
#metaB_vs_metaG <- moments_between_data %>% 
#  mutate(plot = map2(roba, name, ~ ggplot(data = .x) +
#                       aes(x=metab_tara, 
#                           y=metag_tara) +
#                       geom_point() +
#                       scale_x_log10() +
#                       scale_y_log10() + 
#                       theme_bw() +
#           ggtitle(paste0(.y), subtitle = "xylog")))
#ggsave(file="metaB_vs_metaG.pdf", width = 11, 
#       gridExtra::marrangeGrob(grobs = metaB_vs_metaG$plot,  nrow=2, ncol=3, 
#                   top = "metaB and metaG"))
```


```{r c6}
moments_metaBrelGT_stations %>%
  ggplot() +
  aes(x=mean, y=variance) +
  geom_point(aes(col = source), size = 3, alpha = .5) +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggpubr::stat_regline_equation(label.x.npc = "left", label.y.npc = "top") +
  ggpubr::stat_cor(label.x.npc = "middle", label.y.npc = "bottom") +
  theme_bw() +
  scale_x_log10() +
  scale_y_log10() + 
  ggtitle("Mean and Variance",
          subtitle = "All datasets")  +
  guides(colour = guide_legend(override.aes = list(size=3))) +
    labs(caption = "log-log")
```



### 4. Q-Q plots{.tabset}

#### Original

```{r d1}

###plot coi valori originali:

b.means <- moments_metaBrelGT_stations %>% 
  filter(source == "metab_tara") %>% 
  pull(mean)

g.means <- moments_metaBrelGT_stations %>% 
  filter(source=="metag_tara") %>% pull(mean)

t.means <- moments_metaBrelGT_stations %>% 
  filter(source=="metat_tara") %>% 
  pull(mean)


par(mfrow=c(1,3))
qqplot(b.means,g.means, log="xy", main = "metab metag", xlim = c(2e-06, 0.2))
abline(coef = c(0,1))
qqplot(b.means, t.means, log="xy", main = "metab metat", xlim = c(1e-06, 0.2))
abline(coef = c(0,1))
qqplot(g.means,t.means, log="xy", main = "metag metat")
abline(coef = c(0,1))
```


#### Transformed

```{r d2}
###con modifiche:
b.means_minus_mult <- moments_metaBrelGT_stations %>% 
  filter(source=="metab_tara") %>% 
  mutate(mean_plus = (mean - 0.003) *0.004) %>% 
  pull(mean_plus)

t.means_2.5times <- moments_metaBrelGT_stations %>% 
  filter(source=="metat_tara") %>% 
  mutate(mean_multiplied = mean *2.5) %>% 
  pull(mean_multiplied)



par(mfrow=c(1,3))

qqplot(b.means_minus_mult,g.means, log="xy", main = "metab metag")
abline(coef = c(0,1))
qqplot(b.means_minus_mult,t.means_2.5times, log="xy", main = "metab metat")
abline(coef = c(0,1))
qqplot(g.means, t.means_2.5times, log="xy", main = "metag metat")
abline( c(0,1))



moments_metaBrelGT_stations %>% 
  #filter(source %in% c("metag_tara", "metat_tara")) %>% 
  mutate(mean2 = case_when(source == "metat_tara" ~ mean*2.5,
                           source == "metab_tara" ~ (mean - 0.003) *0.004,
                           TRUE ~ mean)) %>% 
  ggplot() +
  aes(x=mean2, fill=source) +
  geom_density(alpha= 0.2) +
  scale_x_log10() +
  geom_rug(aes(col = source)) +
  theme_bw() +
  xlab("mean")
```




<br>

### 5. Relation between moments : skewness-kurtosis{.tabset}

#### metaB
```{r e1}
moments_metab_stations %>%
  ggplot() + 
  aes(x=skewness, y=kurtosis) + 
  #geom_point(col= "gray", size = 1) +
  geom_point(aes(col = richness), size = 3) +
  scale_colour_viridis_c() + 
  geom_smooth(method = lm, formula = y~poly(x,2)) +
  ggpubr::stat_regline_equation(label.x.npc = "left", label.y.npc = "top") +
  ggpubr::stat_cor(label.x.npc = "middle", label.y.npc = "bottom") +
  theme_bw() +
  ggtitle(paste0("Skewness and Kurtosis; ",
                 n_distinct(moments_metab_stations$St.label), " stations"),
          subtitle = ("metaB, diatoms, 20-180, SUR"))
```


#### metaG

```{r e2}

moments_metag_stations %>%
  ggplot() + 
  aes(x=skewness, y=kurtosis) + 
  #geom_point(col = "gray", size = 3) +
  geom_point(aes(col=richness), size=3) +
  scale_color_viridis_c() +
  geom_smooth(method = lm, formula = y~poly(x,2)) +
  ggpubr::stat_regline_equation(label.x.npc = "left", label.y.npc = "top") +
  ggpubr::stat_cor(label.x.npc = "middle", label.y.npc = "bottom") +
  theme_bw() +
  ggtitle(paste0("Skewness and Kurtosis; ",
                 n_distinct(moments_metag_stations$St.label), " stations"),
          subtitle = ("metaG, diatoms, 20-180, SUR"))
```

#### metaT

```{r e3}
moments_metat_stations %>%
  ggplot() + 
  aes(x=skewness, y=kurtosis) + 
  geom_point(aes(col=richness), size = 3) +
  scale_color_viridis_c() +
  geom_smooth(method = lm, formula = y~poly(x,2)) +
  ggpubr::stat_regline_equation(label.x.npc = "left", label.y.npc = "top") +
  ggpubr::stat_cor(label.x.npc = "middle", label.y.npc = "bottom") +
  theme_bw() +
  ggtitle(paste0("Skewness and Kurtosis; ",
                 n_distinct(moments_metat_stations$St.label), " stations"),
          subtitle = ("metaT, diatoms, 20-180, SUR"))
```



#### P. multistriata

```{r e4}

#### Transcriptomes P.multistriata

library(readxl)
#transcriptomics
p.mu_ts <-read_xlsx("C:/Users/Userszn/Documents/PhD/script/Pseudonitzschia/Transcriptomics/Copy of all.annot.xlsx")
p.mu_ts1 <- na.omit(p.mu_ts)

moments_pn <- p.mu_ts1 %>%
  pivot_longer(M2.4_CE:F50b_SL) %>%
  #filter(value != 0) %>%
  group_by(name) %>%
  summarise(mean = mean(value),
            variance = var(value),
            skewness = skewness(value),
            kurtosis = kurtosis(value)) %>%
  mutate(logme = log10(mean), 
         logvar = log10(variance), 
         source=c("p.multistriata"))


moments_pn %>%
  ggplot() +
  aes(x=skewness, y=kurtosis) + 
  geom_point(col = "gray", size = 3) +
  geom_smooth(method = lm, formula = y~poly(x,2)) +
  ggpubr::stat_regline_equation(label.x.npc = "left", label.y.npc = "top") +
  ggpubr::stat_cor(label.x.npc = "middle", label.y.npc = "bottom") +
  theme_bw() +
  ggtitle(paste0("Skewness and Kurtosis; ",
                 n_distinct(moments_pn$name), " cells"),
          subtitle = ("Transcriptomes, P.multistriata"))
```


#### all

```{r e5}

moments_p.mu_conditions %>% 
  rename(St.label = name) %>% 
  rbind(moments_metaBrelGT_stations) %>%
  ggplot() +
  aes(x=skewness, y=kurtosis) +
  geom_point(aes(col = source), size = 3, alpha = .5) +
  geom_smooth(method = lm, formula = y~poly(x,2)) +
  ggpubr::stat_regline_equation(label.x.npc = "left", label.y.npc = "top") +
  ggpubr::stat_cor(label.x.npc = "middle", label.y.npc = "bottom") +
  theme_bw() +
  ggtitle("Skewness and Kurtosis",
          subtitle = "All datasets")  +
  guides(colour = guide_legend(override.aes = list(size=3)))
```


<br>

<br>

### Among Datasets{.tabset}

#### metaB - metaG

```{r f1}
#metaB vs metaG
moments_metaBrelGT_stations %>%
  group_by(St.label) %>% 
  mutate(datashared = n_distinct(source)) %>% 
  ungroup() %>% 
  filter(datashared == 3) %>% 
  select(St.label, richness, mean, 
         median, variance, IQR, source) %>% 
  pivot_longer(richness:IQR) %>% 
  pivot_wider(names_from = source, values_from = value) %>% 
  ggplot() +
  aes(x=metab_tara, 
      y=metag_tara) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() + 
  theme_bw() +
  facet_wrap(~ name, scales = "free") +
  ggtitle("metaB and metaG", subtitle = "xylog")

#moments_metab_stations <- moments_metab_stations %>% 
#  select(St.label, mean, variance, skewness, kurtosis, richness, logme,
#         logvar, source)


```


#### metaB - metaT

```{r f2}
#metaB vs metaT
moments_metaBrelGT_stations %>%
  group_by(St.label) %>% 
  mutate(datashared = n_distinct(source)) %>% 
  ungroup() %>% 
  filter(datashared == 3) %>% 
  select(St.label, richness, mean, 
         median, variance, IQR, source) %>% 
  pivot_longer(richness:IQR) %>% 
  pivot_wider(names_from = source, values_from = value) %>% 
  ggplot() +
  aes(x=metab_tara, 
      y=metat_tara) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() + 
  theme_bw() +
  facet_wrap(~ name, scales = "free") +
  ggtitle("metaB and metaT", subtitle = "xylog")

```


#### metaG - metaT

```{r f3}
#metaG vs metaT
moments_metaBrelGT_stations %>%
  group_by(St.label) %>% 
  mutate(datashared = n_distinct(source)) %>% 
  ungroup() %>% 
  filter(datashared == 3) %>% 
  select(St.label, richness, mean, 
         median, variance, IQR, source) %>% 
  pivot_longer(richness:IQR) %>% 
  pivot_wider(names_from = source, values_from = value) %>% 
  ggplot() +
  aes(x=metag_tara, 
      y=metat_tara) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() + 
  theme_bw() +
  facet_wrap(~ name, scales = "free") +
  ggtitle("metaG and metaT", subtitle = "xylog")

```












