---
title: "Relation between Moments across Datasets"
subtitle: "Genes/OTU levels: Relation between objects (rows)"
author: "Lucia Campese"
date: "Oct 2020"
output:
  html_document:
    code_folding: hide
    self_contained: true
---

```{r import, include=F}
knitr::opts_chunk$set(message = F, error = F, warning = F, echo = F,
                          cache = T)
```

<style>
.column-left{
  float: left;
  width: 50%;
  text-align: left;
}
.column-right{
  float: right;
  width: 50%;
  text-align: right;
}
</style>

<br>

### Aim 

We want to find the theoretical distributions that better fit our data; to do that, we study the relation between the moments of our distributions (mean and variance, skewness and kurtosis).

<br>

### Datasets
#### metaB: 
V9 region; OTU relative abundances; Diatoms; 20-180, SUR. File: barv2016202_swarm_d1_t100.

#### metaG: 
MATOU-v2 unigene relative abundances (RPKM normalization) renormalized on diatoms total abundance per station; Diatoms; 20-180; SUR.

#### metaT: 
MATOU-v2 unigene relative abundances (RPKM normalization) renormalized on diatoms total abundance per station; Diatoms; 20-180; SUR.

#### Transcriptomics P.multistriata: 
Transcriptomes of P. multistriata (Basu et al, 2017); normalization CPM (Counts Per Million).

<br>



Feature            |  metaB                                  | metaG                                                               | metaT                                                              | Transcriptome
-------------------|-----------------------------------------|---------------------------------------------------------------------|--------------------------------------------------------------------|-----------------
**unit**           |  OTU                                    | unigene                                                             | trascribed unigene                                                 | transcribed gene
**condition**      |  sampling station                       | sampling station                                                    | sampling station                                                   | cell
**normalization**  |  TSS                                    | RPKM+TSS                                                            | RPKM+TSS                                                           | CPM
**value type**     |  rel.abundance                          | rel.abundance                                                       | rel. abundance                                                     | rel. abundance
**applied filter** |  OTUs occurring in at least 20 stations | unigenes in common with metaT and occurring in at least 20 stations |unigenes in common with metaG and occurring in at 20 least stations | none 

<br>

<br>

<br>

<br>

## B) Genes/OTU levels: Relation between objects (rows)

How can we address whether the variability we observe between genes is linked to the response of the organisms to the abiotic and biotic environment or to stochastic statistical fluctuations?

<br>


### 1. Occupancy{.tabset}

#### metaB
```{r a1}
library(tidyverse)
library(data.table)
library(e1071)
library(readxl)


#metab
metab <- fread("C:/Users/Userszn/Documents/PhD/TARA_Data/metaB/diatoms/barv2016202_swarm_d1_t100.txt", 
               sep = " ", stringsAsFactors = F) 


metab1 <- metab %>% 
  rename(OTU = V1) %>% 
  #pivot_longer(`TARA_158_SRF_20-180`:`TARA_078_DCM_20-180`) %>% 
  gather(key = name, value = value, -OTU) %>% 
  filter(grepl("SRF", name), value >0) %>% 
  separate(name, into = c("TARA", "St.label", "roba", "roba2"), sep = "_") %>% 
  select(OTU, St.label, value)

metabrelab.tsh20 <- metab1 %>% 
  group_by(OTU) %>% 
  mutate(occupancy = n_distinct(St.label)) %>% 
  ungroup() %>% 
  filter(occupancy > 19) %>% 
  group_by(St.label) %>% 
  mutate(relab = value/sum(value)) %>% 
  ungroup %>% 
  select(OTU, St.label, relab)


metab.tsh20_occupancy <- metabrelab.tsh20 %>% 
  group_by(OTU) %>% 
  summarise(n_stations = n_distinct(St.label))

metab.tsh20_occupancy_table <- metab.tsh20_occupancy %>% 
  select(n_stations) %>% 
  rename("n of stations" = n_stations) %>% 
  summary()

metab.tsh20_occupancy %>% 
  ggplot() +
  aes(x = n_stations) +
  geom_histogram(aes(y = ..density..),
                 bins = 100, 
                 color = "grey30", 
                 fill = "white") +
  geom_density(alpha = .2, fill = "antiquewhite3") +
  xlab("n of stations") +
  theme_bw() +
  ggtitle(paste0("OTUs occupancy; ", n_distinct(metab.tsh20_occupancy$OTU), " OTUs"),
          subtitle = "metaB, Diatoms; 20-180um, SUR") +
  annotation_custom(gridExtra::tableGrob(metab.tsh20_occupancy_table), xmin=50, xmax=75, 
                    ymin=0.4, ymax=0.06)
```

#### metaG

```{r a2}
#falkor
###metaG
library(tidyverse)
library(data.table)
library(e1071)

metag <- fread("C:/Users/Userszn/Documents/PhD/script/metaB_metaG_metaT_cfrall/tables_Samir/table_metaG_TSS_samegenes.csv")


metag.tsh20 <- metag %>% 
  pivot_longer("007":"210") %>% 
  rename(St.label = name) %>% 
  filter(value > 0)

metag.tsh20_occupancy <- metag.tsh20 %>% 
  group_by(geneid) %>% 
  summarise(n_stations = n_distinct(St.label))

metag.tsh20_occupancy_table <- metag.tsh20_occupancy %>% 
  select(n_stations) %>% 
  rename("n of stations" = n_stations) %>% 
  summary()

metag.tsh20_occupancy %>% 
  ggplot() +
  aes(x = n_stations) +
  geom_histogram(aes(y = ..density..),
                 bins = 100, 
                 color = "grey30", 
                 fill = "white") +
  geom_density(alpha = .2, fill = "antiquewhite3") +
  xlab("n of stations") +
  theme_bw() +
  ggtitle(paste0("unigene occupancy; ", n_distinct(metag.tsh20_occupancy$geneid), " unigenes"),
          subtitle = "metaG, Diatoms; 20-180um, SUR") +
  annotation_custom(gridExtra::tableGrob(metag.tsh20_occupancy_table), xmin=50, xmax=75, 
                    ymin=0.4, ymax=0.06)
```


#### metaT
```{r a3}
metat <- fread("C:/Users/Userszn/Documents/PhD/script/metaB_metaG_metaT_cfrall/tables_Samir/table_metaT_TSS_samegenes.csv")


metat.tsh20 <- metat %>% 
  pivot_longer("007":"210") %>% 
  rename(St.label = name) %>% 
  filter(value > 0)

metat.tsh20_occupancy <- metat.tsh20 %>% 
  group_by(geneid) %>% 
  summarise(n_stations = n_distinct(St.label))

metat.tsh20_occupancy_table <- metat.tsh20_occupancy %>% 
  select(n_stations) %>% 
  rename("n of stations" = n_stations) %>% 
  summary()

metat.tsh20_occupancy %>% 
  ggplot() +
  aes(x = n_stations) +
  geom_histogram(aes(y = ..density..),
                 bins = 100, 
                 color = "grey30", 
                 fill = "white") +
  geom_density(alpha = .2, fill = "antiquewhite3") +
  xlab("n of stations") +
  theme_bw() +
  ggtitle(paste0("unigene occupancy; ", n_distinct(metat.tsh20_occupancy$geneid), " unigenes"),
          subtitle = "metaT, Diatoms; 20-180um, SUR") +
  annotation_custom(gridExtra::tableGrob(metat.tsh20_occupancy_table), xmin=50, xmax=75, 
                    ymin=0.4, ymax=0.06)
```


### 2. Relation between moments: mean-variance{.tabset} 

#### metaB

```{r c1}
moments_metab.tsh20_otus <- metabrelab.tsh20 %>% 
  group_by(OTU) %>%
  summarise(mean = mean(relab),
            variance = var(relab),
            skewness = skewness(relab),
            kurtosis = kurtosis(relab),
            n_stations = n_distinct(St.label)) %>%
  mutate(logme = log10(mean), logvar = log10(variance),
         source = c("metab_tara")) %>% 
  na.omit()

lm.metab.meanvar <-lm(formula = log10(moments_metab.tsh20_otus$variance) ~ log10(moments_metab.tsh20_otus$mean))

moments_metab.tsh20_otus %>%
  ggplot() + 
  aes(x=mean, y=variance) + 
  geom_point(aes(col=n_stations), size = 0.5) +
  scale_colour_viridis_c() +
  geom_smooth(method = "lm", formula = y ~ x) +
  theme_bw() +
  scale_x_log10() +
  scale_y_log10() +
  ggtitle(paste0("Mean and Variance; ",
                 n_distinct(moments_metab.tsh20_otus$OTU), " OTUs"),
          subtitle = ("metaB, diatoms, 20-180, SUR")) +
   geom_label(aes(x = 0.0001, y = 1e-02), hjust = 0,
             label = paste("y = ", signif(lm.metab.meanvar$coef[[1]],5), 
      "x +", signif(lm.metab.meanvar$coef[[2]], 5),
      "\nAdj R2 = ", signif(summary(lm.metab.meanvar)$adj.r.squared, 5),
      " \nP < 2.2e-16"))
```


#### metaG

```{r c2, eval=TRUE}
moments_metag.tsh20 <- metag.tsh20 %>%
  group_by(geneid) %>%
  summarise(mean = mean(value),
            variance = var(value),
            skewness = skewness(value),
            kurtosis = kurtosis(value),
            n_stations = n_distinct(St.label)) %>%
  mutate(logme = log10(mean), logvar = log10(variance),
         source = c("metag_tara")) %>% 
  na.omit()


lm.metag.meanvar <-lm(formula = log10(moments_metag.tsh20$variance) ~ log10(moments_metag.tsh20$mean))

moments_metag.tsh20 %>%
  ggplot() + 
  aes(x=mean, y =variance) + 
  geom_point(aes(col=n_stations), size = 0.5) +
  scale_colour_viridis_c() +
  geom_smooth(method = "lm", formula = y ~ x) +
  theme_bw() +
  scale_x_log10() +
  scale_y_log10() +
  ggtitle(paste0("Mean and Variance; ",
                 n_distinct(moments_metag.tsh20$geneid), " unigenes"),
          subtitle = ("metaG, diatoms, 20-180, SUR")) +
   geom_label(aes(x = 0.001, y = 1e-02), hjust = 0,
             label = paste("y = ", signif(lm.metag.meanvar$coef[[1]],5), 
      "x +", signif(lm.metag.meanvar$coef[[2]], 5),
      "\nAdj R2 = ", signif(summary(lm.metag.meanvar)$adj.r.squared, 5),
      " \nP < 2.2e-16"))
```

#### metaT
```{r c3, eval=TRUE}
moments_metat.tsh20 <- metat.tsh20 %>%
  group_by(geneid) %>%
  summarise(mean = mean(value),
            variance = var(value),
            skewness = skewness(value),
            kurtosis = kurtosis(value),
            n_stations = n_distinct(St.label)) %>%
  mutate(logme = log10(mean), logvar = log10(variance),
         source = c("metat_tara")) %>% 
  na.omit()


lm.metat.meanvar <-lm(formula = log10(moments_metat.tsh20$variance) ~ log10(moments_metat.tsh20$mean))

moments_metat.tsh20 %>%
  ggplot() + 
  aes(x=mean, y =variance) + 
  geom_point(aes(col=n_stations), size = 0.5) +
  scale_colour_viridis_c() +
  geom_smooth(method = "lm", formula = y ~ x) +
  theme_bw() +
  scale_x_log10() +
  scale_y_log10() +
  ggtitle(paste0("Mean and Variance; ",
                 n_distinct(moments_metat.tsh20$geneid), " unigenes"),
          subtitle = ("metaT, diatoms, 20-180, SUR")) +
   geom_label(aes(x = 0.001, y = 1e-02), hjust = 0,
             label = paste("y = ", signif(lm.metat.meanvar$coef[[1]],5), 
      "x +", signif(lm.metat.meanvar$coef[[2]], 5),
      "\nAdj R2 = ", signif(summary(lm.metat.meanvar)$adj.r.squared, 5),
      " \nP < 2.2e-16"))
```


#### P.multistriata

```{r c4}
#transcriptomics
p.mu_ts <-read_xlsx("C:/Users/Userszn/Documents/PhD/script/Pseudonitzschia/Transcriptomics/Copy of all.annot.xlsx")
p.mu_ts1 <- na.omit(p.mu_ts)

moments_pn <- p.mu_ts1 %>%
  pivot_longer(M2.4_CE:F50b_SL) %>%
  #filter(value != 0) %>%
  group_by(Row.names) %>%
  summarise(mean = mean(value),
            variance = var(value),
            skewness = skewness(value),
            kurtosis = kurtosis(value)) %>%
  mutate(logme = log10(mean), 
         logvar = log10(variance), 
         source=c("p.multistriata")) %>% 
  rename(geneid = Row.names) %>% 
  na.omit()

lm.pn.meanvar <-lm(formula = log10(moments_pn$variance) ~ log10(moments_pn$mean))


moments_pn %>%
  ggplot() + 
  aes(x=mean, y =variance) + 
  geom_point(col = "gray", size = 0.1) +
  geom_smooth(method = "lm", formula = y ~ x) +
  theme_bw() +
  scale_x_log10() +
  scale_y_log10() +
  ggtitle(paste0("Mean and Variance; ",
                 n_distinct(moments_pn$geneid), " genes"),
          subtitle = ("Transcriptomes, P.multistriata")) +
   geom_label(aes(x = 0.01, y = 1e+06), hjust = 0,
             label = paste("y = ", signif(lm.pn.meanvar$coef[[1]],5), 
      "x +", signif(lm.pn.meanvar$coef[[2]], 5),
      "\nAdj R2 = ", signif(summary(lm.pn.meanvar)$adj.r.squared, 5),
      " \nP < 2.2e-16"))
```


#### All

```{r c5}
library(gridExtra)

#In order to allow a better comparison of the above shown results across all the datasets, divide, in each dataset, values of each unit (OTU/unigene/gene) by the mean of abundance of all units in each condition (sampling station/cell)

#metab
metabrelab.tsh20_rescaled <- metabrelab.tsh20 %>% 
  group_by(St.label) %>% 
  mutate(mean = mean(relab),
         value2 = relab/mean) %>% 
  ungroup() %>% 
  select(OTU, St.label, value2)


moments_metabrelab.tsh20_rescaled <- metabrelab.tsh20_rescaled %>% 
  group_by(OTU) %>%
  summarise(mean = mean(value2),
            variance = var(value2),
            skewness = skewness(value2),
            kurtosis = kurtosis(value2),
            n_stations = n_distinct(St.label)) %>%
  mutate(logme = log10(mean), logvar = log10(variance),
         source = c("metab_tara"))

#metag
metag.tsh20_rescaled <- metag.tsh20 %>% 
  group_by(St.label) %>% 
  mutate(mean = mean(value),
         value2 = value/mean) %>% 
  ungroup() %>% 
  select(geneid, St.label, value2)

moments_metag.tsh20_rescaled <- metag.tsh20_rescaled %>% 
  group_by(geneid) %>%
  summarise(mean = mean(value2),
            variance = var(value2),
            skewness = skewness(value2),
            kurtosis = kurtosis(value2),
            n_stations = n_distinct(St.label)) %>%
  mutate(logme = log10(mean), logvar = log10(variance),
         source = c("metag_tara"))  

#metat
metat.tsh20_rescaled <- metat.tsh20 %>% 
  group_by(St.label) %>% 
  mutate(mean = mean(value),
         value2 = value/mean) %>% 
  ungroup() %>% 
  select(geneid, St.label, value2)

moments_metat.tsh20_rescaled <- metat.tsh20_rescaled %>% 
  group_by(geneid) %>%
  summarise(mean = mean(value2),
            variance = var(value2),
            skewness = skewness(value2),
            kurtosis = kurtosis(value2),
                        n_stations = n_distinct(St.label)) %>%
  mutate(logme = log10(mean), logvar = log10(variance),
         source = c("metat_tara"))

#transcriptmioc data are already ok

moments_metabrelab.tsh20_rescaled <- moments_metabrelab.tsh20_rescaled %>% 
  rename(geneid = OTU)

moments_pn1 <- moments_pn %>% 
  mutate(n_stations = as.numeric(c("16"))) %>% 
  select(geneid, mean, variance, skewness, kurtosis, n_stations, logme, logvar, source)

all_data <- rbind(moments_metabrelab.tsh20_rescaled,
      moments_metag.tsh20_rescaled,
      moments_metat.tsh20_rescaled,
      moments_pn1)

counts <- all_data %>% 
  group_by(source) %>% 
  count()


lm.all.meanvar <-lm(formula = log10(all_data$variance) ~ log10(all_data$mean))


all_data %>%
  ggplot() + 
  aes(x=mean, y=variance) + 
  geom_point(aes(col = source), size = 0.5, alpha = .5) +
  theme_bw() +
  scale_x_log10() +
  scale_y_log10() +
  annotation_custom(tableGrob(counts, rows=NULL,
                              theme = ttheme_default(base_size = 8, 
                                                     base_colour = "black",
                                                     base_family = "",
                                                     parse = FALSE,
                                                     padding = unit(c(4, 4), "mm"))),
                    xmin=log10(1e+01), 
                    xmax=log10(1e+03), 
                    ymin=log10(1.5e-02), 
                    ymax=log10(1e-02)) +
  geom_smooth(method = "lm", formula = y ~ x) +
  ggtitle("Mean and Variance",
          subtitle = "All datasets")  +
  guides(colour = guide_legend(override.aes = list(size=3))) +
   geom_label(aes(x = 1e-01, y = 1e+07), hjust = 0,
             label = paste("y = ", signif(lm.all.meanvar$coef[[1]],5), 
      "x +", signif(lm.all.meanvar$coef[[2]], 5),
      "\nAdj R2 = ", signif(summary(lm.all.meanvar)$adj.r.squared, 5),
      "x +", signif(lm.all.meanvar$coef[[2]], 5),
      " \nP < 2.2e-16"))


```

### 3. Relation between moments: Skewness-Kurtosis{.tabset}

#### metaB

```{r e1}
lm.metab.sk <-lm(formula = moments_metab.tsh20_otus$kurtosis ~ poly(moments_metab.tsh20_otus$skewness, 2, raw=T))

moments_metab.tsh20_otus %>%
  ggplot() + 
  aes(x=skewness, y=kurtosis) + 
  geom_point(aes(col=n_stations), size = 0.5) +
  scale_colour_viridis_c() +
  geom_smooth(method = "lm", formula = y ~ poly(x,2)) +
  theme_bw() +
  ggtitle(paste0("Skewness and Kurtosis; ",
                 n_distinct(moments_metab.tsh20_otus$OTU), " OTUs"),
          subtitle = ("metaB, diatoms, 20-180, SUR")) +
  geom_label(aes(x = 0, y = 60), hjust = 0,
             label = paste("y = ", signif(lm.metab.sk$coef[[1]],5 ), 
                           "x^2 +", signif(lm.metab.sk$coef[[2]], 5),
                           "x + ", signif(lm.metab.sk$coef[[3]], 5),
                           "\nAdj R2 = ", signif(summary(lm.metab.sk)$adj.r.squared, 5),
                           " \nP < 2.2e-16"))
```

#### metaG
```{r e2, eval=TRUE}
lm.metag.sk <-lm(formula = moments_metag.tsh20$kurtosis ~ poly(moments_metag.tsh20$skewness, 2, raw=T))

moments_metag.tsh20 %>%
  ggplot() + 
  aes(x=skewness, y=kurtosis) + 
  geom_point(aes(col=n_stations), size = 0.5) +
  scale_colour_viridis_c() +
  geom_smooth(method = "lm", formula = y ~ poly(x,2)) +
  theme_bw() +
  ggtitle(paste0("Skewness and Kurtosis; ",
                 n_distinct(moments_metag.tsh20$geneid), " unigenes"),
          subtitle = ("metaG, diatoms, 20-180, SUR")) +
  geom_label(aes(x = 0, y = 40), hjust = 0,
             label = paste("y = ", signif(lm.metag.sk$coef[[1]],5 ), 
                           "x^2 +", signif(lm.metag.sk$coef[[2]], 5),
                           "x + ", signif(lm.metag.sk$coef[[3]], 5),
                           "\nAdj R2 = ", signif(summary(lm.metag.sk)$adj.r.squared, 5),
                           " \nP < 2.2e-16"))
```


#### metaT
```{r e4, eval=TRUE}
lm.metat.sk <-lm(formula = moments_metat.tsh20$kurtosis ~ poly(moments_metat.tsh20$skewness, 2, raw=T))

moments_metat.tsh20 %>%
  ggplot() + 
  aes(x=skewness, y=kurtosis) + 
  geom_point(aes(col=n_stations), size = 0.5) +
  scale_colour_viridis_c() +
  geom_smooth(method = "lm", formula = y ~ poly(x,2)) +
  theme_bw() +
  ggtitle(paste0("Skewness and Kurtosis; ",
                 n_distinct(moments_metat.tsh20$geneid), " unigenes"),
          subtitle = ("metaT, diatoms, 20-180, SUR")) +
  geom_label(aes(x = 0, y = 40), hjust = 0,
             label = paste("y = ", signif(lm.metat.sk$coef[[1]],5 ), 
                           "x^2 +", signif(lm.metat.sk$coef[[2]], 5),
                           "x + ", signif(lm.metat.sk$coef[[3]], 5),
                           "\nAdj R2 = ", signif(summary(lm.metat.sk)$adj.r.squared, 5),
                           " \nP < 2.2e-16"))
```


#### P.multistriata
```{r e5}

lm.pn.sk <-lm(formula = moments_pn$kurtosis ~ poly(moments_pn$skewness, 2, raw=T))

moments_pn %>%
  ggplot() + 
  aes(x=skewness, y=kurtosis) + 
  geom_point(col = "gray", size = 0.1) +
  geom_smooth(method = "lm", formula = y ~ poly(x,2)) +
  theme_bw() +
  ggtitle(paste0("Skewness and Kurtosis; ",
                 n_distinct(moments_pn$geneid), " genes"),
          subtitle = ("Transcriptomes, P.multistriata"))  +
  geom_label(aes(x = -1, y = 5), hjust = 0,
             label = paste("y = ", signif(lm.pn.sk$coef[[1]],5 ), 
                           "x^2 +", signif(lm.pn.sk$coef[[2]], 5),
                           "x + ", signif(lm.pn.sk$coef[[3]], 5),
                           "\nAdj R2 = ", signif(summary(lm.pn.sk)$adj.r.squared, 5),
                           " \nP < 2.2e-16"))
```


#### All

```{r e6}
all_data.sk <-lm(formula = all_data$kurtosis ~ poly(all_data$skewness, 2, raw=T))

all_data %>%
  ggplot() + 
  aes(x=skewness, y=kurtosis) + 
  geom_point(aes(col = source), size = .5, alpha = .3) +
  geom_smooth(method = "lm", formula = y ~ poly(x,2)) +
  theme_bw() +
  annotation_custom(tableGrob(counts, rows=NULL,
                              theme = ttheme_default(base_size = 8, 
                                                     base_colour = "black",
                                                     base_family = "",
                                                     parse = FALSE,
                                                     padding = unit(c(4, 4), "mm"))),
                    xmin=0, 
                    xmax=2, 
                    ymin=25, 
                    ymax=45) +
  #facet_wrap(~source, nrow = 4) +
  ggtitle("Skewness and Kurtosis",
          subtitle = "All datasets") +
   guides(colour = guide_legend(override.aes = list(size=3)))  +
  geom_label(aes(x = -1, y = 55), hjust = 0,
             label = paste("y = ", signif(all_data.sk$coef[[1]],5 ), 
                           "x^2 +", signif(all_data.sk$coef[[2]], 5),
                           "x + ", signif(all_data.sk$coef[[3]], 5),
                           "\nAdj R2 = ", signif(summary(all_data.sk)$adj.r.squared, 5),
                           " \nP < 2.2e-16"))
```
