---
title: "Relation between Moments across Datasets"
subtitle: "TSS from abs values; Dataset 1: thsh 10"
author: "Lucia Campese"
date: "Jul 2021"
output:
  html_document:
    code_folding: hide
---

```{r import, include=F}
knitr::opts_chunk$set(message = F, error = F, warning = F, echo = F,
                          cache = T)
```

<style>
.column-left{
  float: left;
  width: 50%;
  text-align: left;
}
.column-right{
  float: right;
  width: 50%;
  text-align: right;
}
</style>

<br>

### Aim 

We want to find the theoretical distributions that better fit our data; to do that, we study the relation between the moments of our distributions (mean and variance, skewness and kurtosis).

<br>

### Datasets
#### metaB: 
V9 region; OTU relative abundances; Diatoms; 20-180, SUR. File: barv2016202_swarm_d1_t100.

#### metaG: 
MATOU-v2 unigene relative abundances (RPKM normalization) renormalized on diatoms total abundance per station; Diatoms; 20-180; SUR

#### metaT: 
MATOU-v2 unigene relative abundances (RPKM normalization) renormalized on diatoms total abundance per station; Diatoms; 20-180; SUR



### Note:
the three dataset have been filtered in the following way:

1. Abundance filter: keep, in each station, only OTUs/unigenes with readcounts > 10 [this reduces the local effect of tails of rare OTUs/unigenes while keeping them at global scale]

2. Also, for metaT: keep only unigenes that are present in metaG [biological criterion]

(v.script file:///C:/Users/Userszn/Documents/PhD/Thesis_writing/1st_Chapter/scripts/make_thsh_all.R)
<br>



Feature    | metaB                | metaG             | metaT              
---------- | -------------------- | ----------------- |------------------- 
unit       | OTU                  | unigene           | trascribed unigene  
condition  | sampling station     | sampling station  | sampling station  
value type | rel.ab (sum per st=1)| rel.ab (RPKM+dia) | rel.ab(RPKM+dia)   


<br>

<br>

## A) Community level: Relation between variables (columns)

How can we address whether the variability we observe between sampling stations is due to a real biological signal or to background noise/technical biases?



### 1. Richness{.tabset}

#### metaB

```{r a1}
library(tidyverse)
library(data.table)
library(e1071)
library(readxl)
load("C:/Users/Userszn/Documents/PhD/Thesis_writing/1st_Chapter/scripts/after_thsh/metab_thsh10.RData")

metab_thsh10_relab <- metab_thsh10 %>% 
  group_by(St.label) %>% 
  mutate(relab = value/sum(value)) %>% 
  ungroup


metab_thsh10_richness <- metab_thsh10_relab %>% 
  group_by(St.label) %>% 
  summarise(n_otus = n_distinct(`OTU/unigene`)) %>% 
  ungroup

metab_thsh10_richness_table <- metab_thsh10_richness %>% 
  select(n_otus) %>% 
  rename("n of OTUs" = n_otus) %>% 
  summary()

metab_thsh10_richness %>% 
  ggplot() +
  aes(x = n_otus) +
  geom_histogram(aes(y = ..density..),
                 bins = 100, 
                 color = "grey30", 
                 fill = "white") +
  geom_density(alpha = .2, fill = "antiquewhite3") +
  xlab("n of OTUs") +
  theme_bw() +
  ggtitle(paste0("Station richness; ", n_distinct(metab_thsh10_richness$St.label), " stations"),
          subtitle = "metaB, Diatoms; 20-180um, SUR") +
  annotation_custom(gridExtra::tableGrob(metab_thsh10_richness_table), xmin=100, xmax=200, 
                    ymin=0.02, ymax=0.03)


```


#### metaG

```{r a2}
load("C:/Users/Userszn/Documents/PhD/Thesis_writing/1st_Chapter/scripts/after_thsh/metag_thsh10.RData")

metag_thsh10.tss <- metag_thsh10 %>% 
  group_by(St.label) %>% 
  mutate(relab = value/sum(value)) %>% 
  ungroup %>% 
  select(-value)

metag_thsh10.tss_richness <- metag_thsh10.tss %>% 
  group_by(St.label) %>% 
  summarise(n_genes = n_distinct(`OTU/unigene`)) %>% 
  ungroup()


metag_thsh10.tss_richness_table <- metag_thsh10.tss_richness %>% 
  select(n_genes) %>% 
  summary()

metag_thsh10.tss_richness %>% 
  ggplot() +
  aes(x = n_genes) +
  geom_histogram(aes(y = ..density..),
                 bins = 100, 
                 color = "grey30", 
                 fill = "white") +
  geom_density(alpha = .2, fill = "antiquewhite3") +
  xlab("n of unigenes") +
  theme_bw() +
  ggtitle(paste0("Station richness; ", n_distinct(metag_thsh10.tss_richness$St.label), " stations"),
          subtitle = "metaG, Diatoms; 20-180um, SUR") +
  annotation_custom(gridExtra::tableGrob(metag_thsh10.tss_richness_table),
                    xmin=100000, xmax=150000, 
                    ymin=5.5e-05, ymax=1e-04)
```

#### metaT 

```{r a3}
load("C:/Users/Userszn/Documents/PhD/Thesis_writing/1st_Chapter/scripts/after_thsh/metat_thsh10_genesmetaG.RData")

metat_thsh10_genesmetaG.tss <- metat_thsh10_genesmetaG %>% 
  group_by(St.label) %>% 
  mutate(relab = value/sum(value)) %>% 
  ungroup %>% 
  select(-value)


metat_thsh10_genesmetaG.tss_richness <- metat_thsh10_genesmetaG.tss %>% 
  group_by(St.label) %>% 
  summarise(n_genes = n_distinct(`OTU/unigene`)) %>% 
  ungroup()


metat_thsh10_genesmetaG.tss_richness_table <- metat_thsh10_genesmetaG.tss_richness %>% 
  select(n_genes) %>% 
  summary()


metat_thsh10_genesmetaG.tss_richness %>% 
  ggplot() +
  aes(x = n_genes) +
  geom_histogram(aes(y = ..density..),
                 bins = 100, 
                 color = "grey30", 
                 fill = "white") +
  geom_density(alpha = .2, fill = "antiquewhite3") +
  xlab("n of unigenes") +
  theme_bw() +
  ggtitle(paste0("Station richness; ", n_distinct(metat_thsh10_genesmetaG.tss_richness$St.label), " stations"),
          subtitle = "metaT, Diatoms; 20-180um, SUR") +
  annotation_custom(gridExtra::tableGrob(metat_thsh10_genesmetaG.tss_richness_table),
                    xmin=100000, xmax=150000,
                    ymin= 0.00005, ymax=0.0001)
```


### 2. RAD{.tabset}

#### metaB

```{r b1}
metab_thsh10_relab %>% 
  group_by(St.label) %>% 
  mutate(richness = n_distinct(`OTU/unigene`)) %>%
  arrange(desc(relab)) %>%
  mutate(Rank = seq_len(n()),
         `log10 of % relative abundance` = log10(relab)) %>%
  ungroup() %>% 
  ggplot() +
  aes(x = Rank, y = `log10 of % relative abundance`,
      col = richness, group = St.label) +
  geom_line(lwd = 0.5, alpha = 0.25) +
  theme_bw() +
  ggtitle("Whittaker (RAD) on diatom OTUs",
          subtitle = "metaB, 20-180, SUR")

```

#### metaG

```{r b2}
metag_thsh10.tss %>%
  group_by(St.label) %>%
  mutate(richness = n_distinct(`OTU/unigene`)) %>%
  arrange(desc(relab)) %>%
  mutate(Rank = seq_len(n()),
         `log10 of % relative abundance` = log10(relab)) %>%
  ggplot() +
  aes(x = Rank, y = `log10 of % relative abundance`,
      col = richness, group = St.label) +
  geom_line(lwd = 0.5, alpha = 0.25) +
  theme_bw() +
  ggtitle("Whittaker (RAD) on diatom unigenes",
          subtitle = "metaG, 20-180, SUR")
```

#### metaT 

```{r b3}
metat_thsh10_genesmetaG.tss %>%
  group_by(St.label) %>%
  mutate(richness = n_distinct(`OTU/unigene`)) %>%
  arrange(desc(relab)) %>%
  mutate(Rank = seq_len(n()),
         `log10 of % relative abundance` = log10(relab)) %>%
  ggplot() +
  aes(x = Rank, y = `log10 of % relative abundance`,
      col = richness, group = St.label) +
  geom_line(lwd = 0.5, alpha = 0.25) +
  theme_bw() +
  ggtitle("Whittaker (RAD) on diatom unigenes",
          subtitle = "metaT, 20-180, SUR")
```


### 3. Relation between moments : mean-variance{.tabset}

#### metaB

```{r c1}
moments_metab_thsh10_stations <- metab_thsh10_relab %>% 
  group_by(St.label) %>%
  summarise(mean = mean(relab),
            median = median(relab),
            variance = var(relab),
            IQR = IQR(relab),
            skewness = skewness(relab),
            kurtosis = kurtosis(relab),
            richness = n_distinct(`OTU/unigene`)) %>%
  mutate(logme = log10(mean), logvar = log10(variance),
         source = c("metab_tara")) %>% 
  na.omit()

lm.metab.meanvar <-lm(formula = log10(moments_metab_thsh10_stations$variance) ~ log10(moments_metab_thsh10_stations$mean))

meanvar.b <- function(.x)  (10**lm.metab.meanvar$coefficients[1]) * .x**lm.metab.meanvar$coefficients[2]

moments_metab_thsh10_stations %>%
  ggplot() + 
  aes(x=mean, y=variance) + 
  geom_point(aes(col = richness), size = 3) +
  scale_colour_viridis_c() + 
  geom_smooth(method = "lm", formula = y ~ x) +
  stat_function(fun = meanvar.b, col = "red", lty = 3) +
  theme_bw() +
  scale_x_log10() +
  scale_y_log10() +
  ggtitle(paste0("Mean and Variance; ",
                 n_distinct(moments_metab_thsh10_stations$St.label), " stations"),
          subtitle = ("metaB, diatoms, 20-180, SUR")) +
  labs(caption = "log-log") +
  geom_label(aes(x = 0.005, y = 0.05), hjust = 0,
             label = paste("y = ",
                           signif(10**lm.metab.meanvar$coef[[1]], 2),
                           "* mean^", signif(lm.metab.meanvar$coef[[2]], 2),
                           "\nAdj R2 = ", signif(summary(lm.metab.meanvar)$adj.r.squared, 3),
                           " \nP < 2.2e-16"))

```

#### metaG

```{r c2}
moments_metag_thsh10_stations <- metag_thsh10.tss %>%
  group_by(St.label) %>%
  summarise(mean = mean(relab),
            median = median(relab),
            variance = var(relab),
            IQR = IQR(relab),
            skewness = skewness(relab),
            kurtosis = kurtosis(relab),
            richness = n_distinct(`OTU/unigene`)) %>%
  mutate(logme = log10(mean), logvar = log10(variance),
         source = c("metag_tara")) %>% 
  na.omit()

lm.metag.meanvar <-lm(formula = log10(moments_metag_thsh10_stations$variance) ~ log10(moments_metag_thsh10_stations$mean))

meanvar.g <- function(.x)  (10**lm.metag.meanvar$coefficients[1]) * .x**lm.metag.meanvar$coefficients[2]

moments_metag_thsh10_stations %>%
  ggplot() + 
  aes(x=mean, y=variance) + 
  geom_point(aes(col=richness), size = 3) +
  stat_function(fun = meanvar.g, col = "red", lty = 3) +
  scale_colour_viridis_c() +
  geom_smooth(method = "lm", formula = y ~ x) +
  theme_bw() +
  scale_x_log10() +
  scale_y_log10() +
  ggtitle(paste0("Mean and Variance; ",
                 n_distinct(moments_metag_thsh10_stations$St.label), " stations"),
          subtitle = ("metaG, diatoms, 20-180, SUR")) +
  labs(caption = "log-log")  +
  geom_label(aes(x = 1e-05, y = 1.5e-05), hjust = 0,
             label = paste("y = ",
                           signif(10**lm.metag.meanvar$coef[[1]], 2),
                           "* mean^", signif(lm.metag.meanvar$coef[[2]], 2),
                           "\nAdj R2 = ", signif(summary(lm.metag.meanvar)$adj.r.squared, 3),
                           " \nP < 2.2e-16"))
```


#### metaT

```{r c3}
moments_metat_thsh10_genesmetaG_stations <- metat_thsh10_genesmetaG.tss %>%
  group_by(St.label) %>%
  summarise(mean = mean(relab),
            median = median(relab),
            variance = var(relab),
            IQR = IQR(relab),
            skewness = skewness(relab),
            kurtosis = kurtosis(relab),
            richness = n_distinct( `OTU/unigene`)) %>%
  mutate(logme = log10(mean), logvar = log10(variance),
         source = c("metat_tara")) %>% 
  na.omit()

lm.metat.meanvar <-lm(formula = log10(moments_metat_thsh10_genesmetaG_stations$variance) ~ log10(moments_metat_thsh10_genesmetaG_stations$mean))

meanvar.t <- function(.x)  (10**lm.metat.meanvar$coefficients[1]) * .x**lm.metat.meanvar$coefficients[2]

moments_metat_thsh10_genesmetaG_stations %>%
  ggplot() + 
  aes(x=mean, y=variance) + 
  geom_point(aes(col=richness), size=3) +
  scale_color_viridis_c() +
  geom_smooth(method = "lm", formula = y ~ x) +
  stat_function(fun = meanvar.t, col = "red", lty = 3) +
  theme_bw() +
  scale_x_log10() +
  scale_y_log10() +
  ggtitle(paste0("Mean and Variance; ",
                 n_distinct(moments_metat_thsh10_genesmetaG_stations$St.label), " stations"),
          subtitle = ("metaT, diatoms, 20-180, SUR")) +
  labs(caption = "log-log") +
  geom_label(aes(x = 1e-05, y = 1e-04), hjust = 0,
             label = paste("y = ",
                           signif(10**lm.metat.meanvar$coef[[1]], 2),
                           "* mean^", signif(lm.metat.meanvar$coef[[2]], 2),
                           "\nAdj R2 = ", signif(summary(lm.metat.meanvar)$adj.r.squared, 3),
                           " \nP < 2.2e-16"))
```



#### all (TARA)

```{r c5}
moments_metaBrelGT_thsh10_stations <- rbind(moments_metab_thsh10_stations,
                                            moments_metag_thsh10_stations,
                                            moments_metat_thsh10_genesmetaG_stations) %>%
  na.omit()


lm.all.meanvar <-lm(formula = log10(moments_metaBrelGT_thsh10_stations$variance) ~ log10(moments_metaBrelGT_thsh10_stations$mean))

meanvar.all <- function(.x)  (10**lm.all.meanvar$coefficients[1]) * .x**lm.all.meanvar$coefficients[2]

moments_metaBrelGT_thsh10_stations %>%
  ggplot() +
  aes(x=mean, y=variance) +
  geom_point(aes(col = source), size = 3, alpha = .5) +
  geom_smooth(method = "lm", formula = y ~ x) +
  stat_function(fun = meanvar.all, col = "red", lty = 3) +
  theme_bw() +
  scale_x_log10() +
  scale_y_log10() + 
  ggtitle("Mean and Variance",
          subtitle = "All datasets")  +
  guides(colour = guide_legend(override.aes = list(size=3))) +
  labs(caption = "log-log") +
  geom_label(aes(x = 1e-05, y = 1e-02), hjust = 0,
             label = paste("y = ",
                           signif(10**lm.all.meanvar$coef[[1]], 2),
                           "* mean^", signif(lm.all.meanvar$coef[[2]], 2),
                           "\nAdj R2 = ", signif(summary(lm.all.meanvar)$adj.r.squared, 3),
                           " \nP < 2.2e-16"))
```



### 4. Q-Q plots{.tabset}

#### Original

```{r d1}
b.means <- moments_metaBrelGT_thsh10_stations %>% 
  filter(source == "metab_tara") %>% 
  pull(mean)

g.means <- moments_metaBrelGT_thsh10_stations %>% 
  filter(source=="metag_tara") %>% pull(mean)

t.means <- moments_metaBrelGT_thsh10_stations %>% 
  filter(source=="metat_tara") %>% 
  pull(mean)


par(mfrow=c(1,3))
qqplot(b.means,g.means, log="xy", main = "metab metag", xlim = c(2e-06, 0.2))
abline(coef = c(0,1))
qqplot(b.means, t.means, log="xy", main = "metab metat", xlim = c(1e-06, 0.2))
abline(coef = c(0,1))
qqplot(g.means,t.means, log="xy", main = "metag metat")
abline(coef = c(0,1))
```


#### Transformed

```{r d2}
b.means_minus_mult <- moments_metaBrelGT_thsh10_stations %>% 
  filter(source=="metab_tara") %>% 
  mutate(mean_plus = (mean - 0.003) *0.004) %>% 
  pull(mean_plus)

t.means_2.5times <- moments_metaBrelGT_thsh10_stations %>% 
  filter(source=="metat_tara") %>% 
  mutate(mean_multiplied = mean *2.5) %>% 
  pull(mean_multiplied)

par(mfrow=c(1,3))

qqplot(b.means_minus_mult,g.means, log="xy", main = "metab metag")
abline(coef = c(0,1))
qqplot(b.means_minus_mult,t.means_2.5times, log="xy", main = "metab metat")
abline(coef = c(0,1))
qqplot(g.means, t.means_2.5times, log="xy", main = "metag metat")
abline( c(0,1))


moments_metaBrelGT_thsh10_stations %>% 
  #filter(source %in% c("metag_tara", "metat_tara")) %>% 
  mutate(mean2 = case_when(source == "metat_tara" ~ mean*2.5,
                           source == "metab_tara" ~ (mean - 0.003) *0.004,
                           TRUE ~ mean)) %>% 
  ggplot() +
  aes(x=mean2, fill=source) +
  geom_density(alpha= 0.2) +
  scale_x_log10() +
  geom_rug(aes(col = source)) +
  theme_bw() +
  xlab("mean")


```




<br>

### 5. Relation between moments : skewness-kurtosis{.tabset}

#### metaB
```{r e1}
lm.metab.sk <-lm(formula = moments_metab_thsh10_stations$kurtosis ~ poly(moments_metab_thsh10_stations$skewness, 2, raw=T))

moments_metab_thsh10_stations %>%
  ggplot() + 
  aes(x=skewness, y=kurtosis) + 
  #geom_point(col= "gray", size = 1) +
  geom_point(aes(col = richness), size = 3) +
  scale_colour_viridis_c() + 
  geom_smooth(method = lm, formula = y~poly(x,2)) +
  theme_bw() +
  ggtitle(paste0("Skewness and Kurtosis; ",
                 n_distinct(moments_metab_thsh10_stations$St.label), " stations"),
          subtitle = ("metaB, diatoms, 20-180, SUR")) +
  geom_label(aes(x = 0, y = 100), hjust = 0,
             label = paste("y = ", signif(lm.metab.sk$coef[[1]], 2), 
                           "x^2 +", signif(lm.metab.sk$coef[[2]], 2),
                           "x + ", signif(lm.metab.sk$coef[[3]], 2),
                           "\nAdj R2 = ", signif(summary(lm.metab.sk)$adj.r.squared, 2),
                           " \nP < 2.2e-16"))
```


#### metaG

```{r e2}
lm.metag.sk <-lm(formula = moments_metag_thsh10_stations$kurtosis ~ poly(moments_metag_thsh10_stations$skewness, 2, raw=T))

moments_metag_thsh10_stations %>%
  ggplot() + 
  aes(x=skewness, y=kurtosis) + 
  #geom_point(col = "gray", size = 3) +
  geom_point(aes(col=richness), size=3) +
  scale_color_viridis_c() +
  geom_smooth(method = lm, formula = y~poly(x,2)) +
  theme_bw() +
  ggtitle(paste0("Skewness and Kurtosis; ",
                 n_distinct(moments_metag_thsh10_stations$St.label), " stations"),
          subtitle = ("metaG, diatoms, 20-180, SUR"))  +
  geom_label(aes(x = 0, y = 20000), hjust = 0,
             label = paste("y = ", signif(lm.metag.sk$coef[[1]], 2), 
                           "x^2 +", signif(lm.metag.sk$coef[[2]], 2),
                           "x + ", signif(lm.metag.sk$coef[[3]], 2),
                           "\nAdj R2 = ", signif(summary(lm.metag.sk)$adj.r.squared, 2),
                           " \nP < 2.2e-16"))

```

#### metaT

```{r e3}
lm.metat.sk <-lm(formula = moments_metat_thsh10_genesmetaG_stations$kurtosis ~ poly(moments_metat_thsh10_genesmetaG_stations$skewness, 2, raw=T))

moments_metat_thsh10_genesmetaG_stations %>%
  ggplot() + 
  aes(x=skewness, y=kurtosis) + 
  geom_point(aes(col=richness), size = 3) +
  scale_color_viridis_c() +
  geom_smooth(method = lm, formula = y~poly(x,2)) +
  theme_bw() +
  ggtitle(paste0("Skewness and Kurtosis; ",
                 n_distinct(moments_metat_thsh10_genesmetaG_stations$St.label), " stations"),
          subtitle = ("metaT, diatoms, 20-180, SUR"))  +
  geom_label(aes(x = 0, y = 6000), hjust = 0,
             label = paste("y = ", signif(lm.metat.sk$coef[[1]], 2), 
                           "x^2 +", signif(lm.metat.sk$coef[[2]], 2),
                           "x + ", signif(lm.metat.sk$coef[[3]], 2),
                           "\nAdj R2 = ", signif(summary(lm.metat.sk)$adj.r.squared, 2),
                           " \nP < 2.2e-16"))
```



#### all (TARA)

```{r e5}
all_data.sk <-lm(formula = moments_metaBrelGT_thsh10_stations$kurtosis ~ poly(moments_metaBrelGT_thsh10_stations$skewness, 2, raw=T))

moments_metaBrelGT_thsh10_stations %>% 
  ggplot() +
  aes(x=skewness, y=kurtosis) +
  geom_point(aes(col = source), size = 3, alpha = .5) +
  geom_smooth(method = lm, formula = y~poly(x,2)) +
  theme_bw() +
  ggtitle("Skewness and Kurtosis",
          subtitle = "All datasets")  +
  guides(colour = guide_legend(override.aes = list(size=3))) +
  geom_label(aes(x = 0, y = 20000), hjust = 0,
             label = paste("y = ", signif(all_data.sk$coef[[1]], 2), 
                           "x^2 +", signif(all_data.sk$coef[[2]], 2),
                           "x + ", signif(all_data.sk$coef[[3]], 2),
                           "\nAdj R2 = ", signif(summary(all_data.sk)$adj.r.squared, 2),
                           " \nP < 2.2e-16"))
```


<br>

<br>

### Among Datasets{.tabset}

#### metaB - metaG

```{r f1}
#metaB vs metaG
moments_metaBrelGT_thsh10_stations %>%
  group_by(St.label) %>% 
  mutate(datashared = n_distinct(source)) %>% 
  ungroup() %>% 
  filter(datashared == 3) %>% 
  select(St.label, richness, mean, 
         median, variance, IQR, source) %>% 
  pivot_longer(richness:IQR) %>% 
  pivot_wider(names_from = source, values_from = value) %>% 
  ggplot() +
  aes(x=metab_tara, 
      y=metag_tara) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() + 
  theme_bw() +
  facet_wrap(~ name, scales = "free") +
  ggtitle("metaB and metaG", subtitle = "xylog")
```


#### metaB - metaT

```{r f2}
#metaB vs metaT
moments_metaBrelGT_thsh10_stations %>%
  group_by(St.label) %>% 
  mutate(datashared = n_distinct(source)) %>% 
  ungroup() %>% 
  filter(datashared == 3) %>% 
  select(St.label, richness, mean, 
         median, variance, IQR, source) %>% 
  pivot_longer(richness:IQR) %>% 
  pivot_wider(names_from = source, values_from = value) %>% 
  ggplot() +
  aes(x=metab_tara, 
      y=metat_tara) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() + 
  theme_bw() +
  facet_wrap(~ name, scales = "free") +
  ggtitle("metaB and metaT", subtitle = "xylog")
```


#### metaG - metaT

```{r f3}
#metaG vs metaT
moments_metaBrelGT_thsh10_stations %>%
  group_by(St.label) %>% 
  mutate(datashared = n_distinct(source)) %>% 
  ungroup() %>% 
  filter(datashared == 3) %>% 
  select(St.label, richness, mean, 
         median, variance, IQR, source) %>% 
  pivot_longer(richness:IQR) %>% 
  pivot_wider(names_from = source, values_from = value) %>% 
  ggplot() +
  aes(x=metag_tara, 
      y=metat_tara) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() + 
  theme_bw() +
  facet_wrap(~ name, scales = "free") +
  ggtitle("metaG and metaT", subtitle = "xylog")
```












