---
title: "Fit per Station"
subtitle: "metaT"
author: "Lucia Campese"
date: "Feb-Mar 2020"
output:
  html_document:
    code_folding: hide
    self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style>
.column-left{
  float: left;
  width: 50%;
  text-align: left;
}
.column-right{
  float: right;
  width: 50%;
  text-align: right;
}
</style>


## Section One: Station-centered analyses

### Dataset
##### Omic data: metaT
##### Taxon: Diatoms
##### Depth: Surface
##### Size fraction: 20-180 um
##### Geographic scale: Global  

<br>

1. Estimate fits

```{r eval=FALSE}
library(data.table)
library(tidyverse)
library(poweRlaw)

print("all stations , explno, vector = 500")
print("upload data")

a <- fread("metat_diatoms_QQSS_SUR_normalized_diatoms_v2.ssv", header = F, stringsAsFactors = F) %>%
  separate(V2, into = c("abundance", "St.label"), sep = "\\s") %>%
  rename(geneid = V1) %>%
  mutate(St.label = as.numeric(sprintf("%03d",as.numeric(St.label))),
         abundance = as.numeric(abundance)) %>%
  filter(St.label != 173)


print("estimate exp, lno and pl fits")

mix <- seq(1,10, length=100) %o% 10^-(3:7) %>% as.vector ##500 punti

estimate_exp <- function(x, y=mix)
{
  m_exp = conexp$new(x)
  est_xmin_exp = estimate_xmin(m_exp, xmins=y)
  m_exp$setXmin(est_xmin_exp)
  est_pars_exp = estimate_pars(m_exp)
  m_exp$setPars(est_pars_exp)
  return(m_exp)
}


estimate_lno <- function(x, y=mix)
  {
  out = conlnorm$new(x)
  xmin <- tryCatch(
    {
    estimate_xmin(out, xmins = y)
    },
    error = function(cond) {
      message("something went wrong.")
      message(cond)
      return(NA)
    })
  if (is.na(xmin)){
      return(xmin)
   } else {
      out$setXmin(xmin)
      est_pars_lno = estimate_pars(out)
      out$setPars(est_pars_lno)
      return(out)
}
}

estimate_pl <-  function(x, y=mix)
{
  m_pl = conpl$new(x)
  est_xmin_pl = estimate_xmin(m_pl, xmins=y)
  m_pl$setXmin(est_xmin_pl)
  est_pars_pl = estimate_pars(m_pl)
  m_pl$setPars(est_pars_pl)
  return(m_pl)
}


b <- a %>%
  group_by(St.label) %>%
  nest() %>%
  ungroup() %>%
  arrange(St.label) %>%
  mutate(m_exp = map(data, ~ estimate_exp (.x$abundance, y=mix)),
         m_lno = map(data, ~ estimate_lno (.x$abundance, y=mix)),
         m_pl = map(data, ~ estimate_pl (.x$abundance, y=mix)))

print("save fits")

save(b,file="fits_all_stations_explno_vector500_metaT.RData")
```

<br>

2. Plot fits

```{r eval=FALSE}
library(tidyverse)
library(data.table)
library(poweRlaw)

richnessinfo <- read.delim("number_diatoms_unigenes_per_station_metaT_QQSS_SUR_v2", header = F,
                    stringsAsFactors = F) %>%
  rename(richness = V1, St.label = V2) %>%
  mutate(St.label = as.numeric(sprintf("%03d",as.numeric(St.label))),
         richness = as.numeric(richness)) %>%
  filter(St.label != " NA")


load("fits_all_stations_explno_vector500_metaT.RData")

d <- inner_join(b, richnessinfo) %>% arrange(richness)

make_plots <- function(x)
{
  plot(d$m_exp[[x]], main=paste0("Station: ", d$St.label[[x]], "; ", d$richness[[x]], " genes"))
  lines(d$m_exp[[x]], col=2, lwd=4)
  lines(d$m_pl[[x]],  col=3, lwd=4)
  text(5e-4,0.1,     labels="exp", col =2)
  text(5e-4,0.9,     labels="power", col =3)
tryCatch (
    {
      lines(d$m_lno[[x]], col=4, lwd=4)
      text(5e-4,0.3,     labels="lognorm", col =4)
      return("ok")
    },
    error = function(cond)
    {
      message("something went wrong.")
      message(cond)
      return(NA)
    })
}


pdf("plots_all_stations_explno_vector500_richness_arranged_metaT.pdf")
lapply(seq_len(nrow(d)), make_plots)
dev.off()
```

![Fits_metaT](C:/Users/Userszn/Google Drive/PhD/script/metaB_metaG_metaT_cfrall/outputs/Per_Station/Fits/metaT/plots_all_stations_explno_vector500_richness_arranged_metaT-pages-deleted.pdf){width=100% height=700}

<br>

3. Extract xmins and pars

```{r eval=FALSE}
library(data.table)
library(poweRlaw)
library(tidyverse)

load("fits_all_stations_explno_vector500_metaT.RData")

###1) Extract xmins

extract_mins_all <- function(x)
{
  unlisted_exp = unlist(b$m_exp[[x]])
  xmin_exp = unlisted_exp$xmin
  
  unlisted_pl = unlist(b$m_pl[[x]])
  xmin_pl = unlisted_pl$xmin
  
  unlisted_lno = unlist(b$m_lno[[x]])
  xmin_lno <- tryCatch(
    {
      unlisted_lno$xmin
    },
    error = function(cond) 
    {
      message("something went wrong.")
      message(cond)
      return(NA)
    })
  if(is.na(xmin_lno))
  {
    return(xmin_lno)
  }
  else
  {
    m <- as.matrix(c("xmin_exp" = xmin_exp, "xmin_pl" = xmin_pl, "xmin_lno" = xmin_lno))
    d <- as.data.frame(m)
    colnames(d) <-paste0("St.", b$St.label[[x]])
    return(d)
  }
}

mins <- lapply(seq_len(nrow(b)), extract_mins_all)

d <- data.frame(lapply(mins, c))
rownames(d) <- c("xmin_exp", "xmin_pl", "xmin_lno")

save(d,file="xmins_all_stations_explno_vector500_metaT.RData")


###2) extract parameters

extract_pars_all <- function(x)
{
  unlisted_exp = unlist(b$m_exp[[x]])
  pars_exp = unlisted_exp$pars
  
  unlisted_pl = unlist(b$m_pl[[x]])
  pars_pl = unlisted_pl$pars
  
  unlisted_lno = unlist(b$m_lno[[x]])
  pars_lno <- tryCatch(
    {
      unlisted_lno$pars
    },
    error = function(cond) 
    {
      message("something went wrong.")
      message(cond)
      return(NA)
    })
  if(is.na(pars_lno))
  {
    return(pars_lno)
  }
  else
  {
    m <- as.matrix(c("pars_exp" = pars_exp, "pars_pl" = pars_pl, "pars_lno" = pars_lno))
    d <- as.data.frame(m)
    colnames(d) <-paste0("St.", b$St.label[[x]])
    return(d)
  }
}

parss <- lapply(seq_len(nrow(b)), extract_pars_all)
d_pars <- as.data.frame(parss)

save(d_pars,file="pars_all_stations_explno_vector500_metaT.RData")
```


<br>

4. Plot xmins per station

```{r eval=FALSE}
setwd("C:/Users/Userszn/Google Drive/PhD/script/metaB_metaG_metaT_cfrall/fit_per_station/metaT")

library(tidyverse)
library(data.table)
library(poweRlaw)
library(ggplot2)
library(ggrepel)

list.files(pattern = ".RData$")

############################ x mins ############################
load("xmins_all_stations_explno_vector500_metaT.RData")

head(d)


###xmins per station
##a.
pdf("metaT_xmins_per_station.pdf", width = 8.5)
as.data.frame(t(d)) %>%
  rename(exponential = xmin_exp,
         powerlaw = xmin_pl,
         lognormal = xmin_lno) %>% 
  rownames_to_column("St.label") %>% 
  gather(Distribution, value, -St.label) %>% 
  arrange(St.label) %>% 
  filter(!is.na(value)) %>% 
  mutate(St.label = substr(St.label, 4,6)) %>% 
  ggplot() +
  geom_point(aes(x=St.label, y=value, col=Distribution),
             size=2.5) +
  scale_color_manual(values = c("red", "blue", "green")) +
  scale_y_log10() +
  theme_minimal() +
  ylab("xmin") +
  theme(axis.text.x=element_text(angle=50, size=7, vjust=0.5)) +
  ggtitle("Diatoms, metaT, 20-180, SUR",
          subtitle = "xmins; ylog")
dev.off()
```
![xmins_station_metaT](C:/Users/Userszn/Google Drive/PhD/script/metaB_metaG_metaT_cfrall/outputs/Per_Station/Fits/metaT/metaT_xmins_per_station.pdf){width=100% height=600}

<br>

5. Plot xmins per richness and normalization factor

```{r eval=FALSE}
###xmins per richness
richnessinfo <- read.delim("C:/Users/Userszn/Google Drive/PhD/script/metaB_metaG_metaT_cfrall/number_diatoms_unigenes_per_station_metaT_QQSS_SUR_v2", header = F,
                           stringsAsFactors = F) %>% 
  rename(richness = V1, St.label = V2) %>% 
  mutate(St.label = sprintf("%03d",as.numeric(St.label)),
         richness = as.numeric(richness)) %>% 
  filter(St.label != " NA")


pdf("metaT_xmins_per_richness.pdf", width = 8.5)
as.data.frame(t(d)) %>%
  rename(exponential = xmin_exp,
         powerlaw = xmin_pl,
         lognormal = xmin_lno) %>% 
  rownames_to_column("St.label") %>% 
  gather(Distribution, value, -St.label) %>% 
  arrange(St.label) %>% 
  filter(!is.na(value)) %>% 
  mutate(St.label= substr(St.label, 4,6)) %>%
  inner_join(richnessinfo) %>% 
  ggplot() +
  geom_point(aes(x=richness, y=value, col=Distribution),
             size=2.5) +
  scale_color_manual(values = c("red", "blue", "green")) +
  scale_y_log10() +
  scale_x_log10() +
  theme_minimal() +
  ylab("xmin") +
  #theme(axis.text.x=element_text(angle=50, size=7, vjust=0.5)) +
  ggtitle("Diatoms, metaT, 20-180, SUR",
          subtitle = "xmins; xylog") +
  facet_wrap(~Distribution, scales = "free")
dev.off()


###xmins per normalization factor
metat_norm_fact <- fread("C:/Users/Userszn/Google Drive/PhD/script/metaB_metaG_metaT_cfrall/metat_diatoms_QQSS_SUR_norm_factors_v2.ssv", stringsAsFactors=F, header=F) %>%
  rename(norm_fact = V1, St.label = V2) %>%
  mutate(St.label = sprintf("%03d", as.numeric(St.label)))

pdf("metaT_xmins_per_norm_fact.pdf", width = 8.5)
as.data.frame(t(d)) %>%
  rename(exponential = xmin_exp,
         powerlaw = xmin_pl,
         lognormal = xmin_lno) %>% 
  rownames_to_column("St.label") %>% 
  gather(Distribution, value, -St.label) %>% 
  arrange(St.label) %>% 
  filter(!is.na(value)) %>% 
  mutate(St.label= substr(St.label, 4,6)) %>%
  inner_join(metat_norm_fact) %>% 
  ggplot() +
  geom_point(aes(x=norm_fact, y=value, col=Distribution),
             size=2.5) +
  scale_color_manual(values = c("red", "blue", "green")) +
  scale_y_log10() +
  scale_x_log10() +
  theme_minimal() +
  ylab("xmin") +
  ggtitle("Diatoms, metaT, 20-180, SUR",
          subtitle = "xmins; xylog") +
  facet_wrap(~Distribution, scales = "free")
dev.off()
```

<div class="column-left">
![xmins_richness_metaT](C:/Users/Userszn/Google Drive/PhD/script/metaB_metaG_metaT_cfrall/outputs/Per_Station/Fits/metaT/metaT_xmins_per_richness.pdf){width=100% height=600}
</div><div class="column-right">
![xmins_normfact_metaT](C:/Users/Userszn/Google Drive/PhD/script/metaB_metaG_metaT_cfrall/outputs/Per_Station/Fits/metaT/metaT_xmins_per_norm_fact.pdf){width=100% height=600}
</div>

<br>
<br>
<br>

6. Plot pars per station

```{r eval=FALSE}
############################ pars ############################
load("pars_all_stations_explno_vector500_metaT.RData")

##pars per station
pdf("metaT_pars_per_station.pdf", width = 8.5)
as.data.frame(t(d_pars)) %>% 
  na.omit(f) %>%  
  rownames_to_column("St.label") %>% 
  select(-c(pars_lno2)) %>% 
  mutate(pars_lno1 = abs(pars_lno1),
         St.label= substr(St.label, 4,6)) %>%
  mutate(St.label = sprintf("%03d", as.numeric(St.label))) %>%
  rename(exponential_lambda = pars_exp,
         lognormal_mu = pars_lno1,
         powerlaw_alpha = pars_pl) %>% 
  gather(Par, value, -St.label) %>% 
  arrange(St.label) %>% 
  filter(!is.na(value)) %>% 
  ggplot() +
  geom_point(aes(x=St.label, y=value, col=Par),
             size=2.5) +
  scale_color_manual(values = c("red", "blue", "green")) +
  scale_y_log10() +
  theme_minimal() +
  theme(axis.text.x=element_text(angle=50, size=7, vjust=0.5)) +
  ggtitle("Diatoms, metaT, 20-180, SUR",
          subtitle = "parameters; ylog")
dev.off()
```

![pars_station_metaT](C:/Users/Userszn/Google Drive/PhD/script/metaB_metaG_metaT_cfrall/outputs/Per_Station/Fits/metaT/metaT_pars_per_station.pdf){width=100% height=600}

<br>

7. Plot pars per richness and normalization factor

```{r eval=FALSE}
###pars per richness
pdf("metaT_pars_per_richness.pdf", width = 8.5)
as.data.frame(t(d_pars)) %>% 
  na.omit(f) %>%  
  rownames_to_column("St.label") %>% 
  select(-c(pars_lno2)) %>% 
  mutate(pars_lno1 = abs(pars_lno1),
         St.label= substr(St.label, 4,6)) %>%
  mutate(St.label = sprintf("%03d", as.numeric(St.label))) %>%
  rename(exponential_lambda = pars_exp,
         lognormal_mu = pars_lno1,
         powerlaw_alpha = pars_pl) %>% 
  gather(Par, value, -St.label) %>% 
  arrange(St.label) %>% 
  filter(!is.na(value)) %>% 
  inner_join(richnessinfo) %>% 
  ggplot() +
  geom_point(aes(x=richness, y=value, col=Par),
             size=2.5) +
  scale_color_manual(values = c("red", "blue", "green")) +
  scale_y_log10() +
  scale_x_log10() +
  theme_minimal() +
  #theme(axis.text.x=element_text(angle=50, size=7, vjust=0.5)) +
  ggtitle("Diatoms, metaT, 20-180, SUR",
          subtitle = "parameters; xylog") +
  facet_wrap(~Par, scales = "free") 
dev.off()


###pars per normalization factor
pdf("metaT_pars_per_norm_fact.pdf", width = 8.5)
as.data.frame(t(d_pars)) %>% 
  na.omit(f) %>%  
  rownames_to_column("St.label") %>% 
  select(-c(pars_lno2)) %>% 
  mutate(pars_lno1 = abs(pars_lno1),
         St.label= substr(St.label, 4,6)) %>%
  mutate(St.label = sprintf("%03d", as.numeric(St.label))) %>%
  rename(exponential_lambda = pars_exp,
         lognormal_mu = pars_lno1,
         powerlaw_alpha = pars_pl) %>% 
  gather(Par, value, -St.label) %>% 
  arrange(St.label) %>% 
  filter(!is.na(value)) %>% 
  inner_join(metat_norm_fact) %>% 
  ggplot() +
  geom_point(aes(x=norm_fact, y=value, col=Par),
             size=2.5) +
  scale_color_manual(values = c("red", "blue", "green")) +
  scale_y_log10() +
  scale_x_log10() +
  theme_minimal() +
  ggtitle("Diatoms, metaT, 20-180, SUR",
          subtitle = "xylog") +
  facet_wrap(~Par, scale="free") 
dev.off()
```

<div class="column-left">
![pars_richness_metaT](C:/Users/Userszn/Google Drive/PhD/script/metaB_metaG_metaT_cfrall/outputs/Per_Station/Fits/metaT/metaT_pars_per_richness.pdf){width=100% height=600}
</div><div class="column-right">
![pars_normfact_metaT](C:/Users/Userszn/Google Drive/PhD/script/metaB_metaG_metaT_cfrall/outputs/Per_Station/Fits/metaT/metaT_pars_per_norm_fact.pdf){width=100% height=600}
</div>

<br>

8. Plot relation between richness and normalization factor

```{r eval=FALSE}
richness_normfact <- inner_join(richnessinfo, metat_norm_fact)
pdf("metaT_richness_vs_normfact.pdf", width = 8.5)
richness_normfact %>%  
  ggplot() + 
  geom_point(aes(x=richness, y=norm_fact)) +
  scale_y_log10() +
  scale_x_log10() +
  theme_minimal() +
  ylab("normalization factor") +
  ggtitle("Diatoms, metaT, 20-180, SUR",
          subtitle = "xylog") +
    geom_label_repel(aes(x=richness, y=norm_fact), col  = "gray21",
                   label=richness_normfact$St.label,
                   fontface=2, size = 3)
dev.off()
```
![richness_normfact_metaT](C:/Users/Userszn/Google Drive/PhD/script/metaB_metaG_metaT_cfrall/outputs/Per_Station/Fits/metaT/metaT_richness_vs_normfact.pdf){width=100% height=600}


