---
title: "Fit per Station"
subtitle: "metaB"
author: "Lucia Campese"
date: "Feb-Mar 2020"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style>
.column-left{
  float: left;
  width: 50%;
  text-align: left;
}
.column-right{
  float: right;
  width: 50%;
  text-align: right;
}
</style>


## Section One: Station-centered analyses

### Dataset
##### Omic data: metaB
##### Taxon: Diatoms
##### Depth: Surface
##### Size fraction: 20-180 um
##### Geographic scale: Global  

<br>

1. Estimate fits

```{r eval=FALSE}
library(data.table)
library(tidyverse)
library(poweRlaw)

print("upload datasets")

##metaB
metab_reads <- read.delim(file="diatoms.txt", sep = " ", stringsAsFactors = F) %>%
  select(contains("_"))

#upload environmental data and filter
dat_samp <- read.delim("dat_samp.txt") %>%
  filter(Depth  == "SRF", Fraction.size == "20-180") %>%
  rename(St.label = Station.label) %>%
  mutate(St.label = sprintf("%03d", as.numeric(substr(St.label, 6, 8)))) %>%
  select(Sample.id, St.label)


###filter metab
metab2 <- metab_reads[,names(metab_reads)%in%dat_samp$Sample.id] %>%
  rownames_to_column("cid") %>%
  gather (Sample.id, values, -cid) %>%
  merge(dat_samp) %>%
  filter(values >0) %>%
  group_by(St.label) %>%
  mutate(relab = values/sum(values),
         richness = n_distinct(cid)) %>%
  select(-c(Sample.id, values)) %>%
  ungroup()


mix <- seq(1,10, length=100) %o% 10^-(3:7) %>% as.vector ##500 punti

print("estimate fits")

estimate_exp <- function(x, y=mix)
{
  m_exp = conexp$new(x)
  print("exp")
  est_xmin_exp = estimate_xmin(m_exp, xmins=y)
  m_exp$setXmin(est_xmin_exp)
  est_pars_exp = estimate_pars(m_exp)
  m_exp$setPars(est_pars_exp)
  return(m_exp)
}

estimate_lno <- function(x, y=mix)
{
  out = conlnorm$new(x)
  xmin <- tryCatch(
    {
      estimate_xmin(out, xmins = y)
    },
    error = function(cond) {
      message("something went wrong.")
      message(cond)
      return(NA)
    })
  if (is.na(xmin)){
    return(xmin)
  } else {
    out$setXmin(xmin)
    est_pars_lno = estimate_pars(out)
    out$setPars(est_pars_lno)
    return(out)
  }
}


estimate_pl <-  function(x, y=mix)
{
  m_pl = conpl$new(x)
  est_xmin_pl = estimate_xmin(m_pl, xmins=y)
  m_pl$setXmin(est_xmin_pl)
  est_pars_pl = estimate_pars(m_pl)
  m_pl$setPars(est_pars_pl)
  return(m_pl)
}



b <- metab2 %>%
  group_by(St.label) %>%
  nest() %>%
  ungroup() %>%
  arrange(St.label) %>%
  mutate(m_exp = map(data, ~ estimate_exp (.x$relab, y=mix)),
         m_lno = map(data, ~ estimate_lno (.x$relab, y=mix)),
         m_pl = map(data, ~ estimate_pl (.x$relab, y=mix)))


print("save fits")

save(b,file="fits_all_stations_explno_vector500_metaB_richness.RData")
```

<br>

2. Plot fits

```{r eval=FALSE}
library(tidyverse)
library(data.table)
library(poweRlaw)


load("fits_all_stations_explno_vector500_metaB_richness.RData")


make_plots <- function(x)
{
  plot(d$m_exp[[x]], main=paste0("Station: ", d$St.label[[x]], "; ", d$richness[[x]], " OTUs"))
  lines(d$m_exp[[x]], col=2, lwd=4)
  lines(d$m_pl[[x]],  col=3, lwd=4)
  text(5e-2,0.1,     labels="exp", col =2)
  text(5e-2,0.9,     labels="power", col =3)
tryCatch (
    {
      lines(d$m_lno[[x]], col=4, lwd=4)
      text(5e-2,0.3,     labels="lognorm", col =4)
      return("ok")
    },
    error = function(cond)
    {
      message("something went wrong.")
      message(cond)
      return(NA)
    })
}

pdf("plots_all_stations_explno_vector500_metaB_richness.pdf")
lapply(seq_len(nrow(d)), make_plots)
dev.off()
```

![Fits_metaB](C:/Users/Userszn/Google Drive/PhD/script/metaB_metaG_metaT_cfrall/outputs/Per_Station/Fits/metaB/plots_all_stations_explno_vector500_metaB_richness_arranged_type_p.pdf){width=100% height=700}

<br>

3. Extract xmins and pars

```{r eval=FALSE}
library(data.table)
library(poweRlaw)
library(tidyverse)

load("fits_all_stations_explno_vector500_metaB_richness.RData")

###1) Extract xmins

extract_mins_all <- function(x)
{
  unlisted_exp = unlist(b$m_exp[[x]])
  xmin_exp = unlisted_exp$xmin
  
  unlisted_pl = unlist(b$m_pl[[x]])
  xmin_pl = unlisted_pl$xmin
  
  unlisted_lno = unlist(b$m_lno[[x]])
  xmin_lno <- tryCatch(
    {
      unlisted_lno$xmin
    },
    error = function(cond) 
    {
      message("something went wrong.")
      message(cond)
      return(NA)
    })
  if(is.na(xmin_lno))
  {
    return(xmin_lno)
  }
  else
  {
    m <- as.matrix(c("xmin_exp" = xmin_exp, "xmin_pl" = xmin_pl, "xmin_lno" = xmin_lno))
    d <- as.data.frame(m)
    colnames(d) <-paste0("St.", b$St.label[[x]])
    return(d)
  }
}

mins <- lapply(seq_len(nrow(b)), extract_mins_all)

d <- data.frame(lapply(mins, c))
rownames(d) <- c("xmin_exp", "xmin_pl", "xmin_lno")

save(d,file="xmins_all_stations_explno_vector500_metaB.RData")

###2) extract parameters

extract_pars_all <- function(x)
{
  unlisted_exp = unlist(b$m_exp[[x]])
  pars_exp = unlisted_exp$pars
  
  unlisted_pl = unlist(b$m_pl[[x]])
  pars_pl = unlisted_pl$pars
  
  unlisted_lno = unlist(b$m_lno[[x]])
  pars_lno <- tryCatch(
    {
      unlisted_lno$pars
    },
    error = function(cond) 
    {
      message("something went wrong.")
      message(cond)
      return(NA)
    })
  if(is.na(pars_lno))
  {
    return(pars_lno)
  }
  else
  {
    m <- as.matrix(c("pars_exp" = pars_exp, "pars_pl" = pars_pl, "pars_lno" = pars_lno))
    d <- as.data.frame(m)
    colnames(d) <-paste0("St.", b$St.label[[x]])
    return(d)
  }
}

parss <- lapply(seq_len(nrow(b)), extract_pars_all)
d_pars <- as.data.frame(parss)

save(d_pars,file="pars_all_stations_explno_vector500_metaB.RData")
```


4. Plot xmins per station

```{r eval=FALSE}
setwd("C:/Users/Userszn/Google Drive/PhD/script/metaB_metaG_metaT_cfrall/fit_per_station/metaB")

library(tidyverse)
library(data.table)
library(poweRlaw)
library(ggplot2)
library(ggrepel)

list.files(pattern = ".RData$")

############################ x mins ############################
load("xmins_all_stations_explno_vector500_metaB.RData")

###xmins per station
##a.
pdf("metaB_xmins_per_station.pdf", width = 8.5)
as.data.frame(t(d)) %>%
  rename(exponential = xmin_exp,
         powerlaw = xmin_pl,
         lognormal = xmin_lno) %>% 
  rownames_to_column("St.label") %>% 
  gather(Distribution, value, -St.label) %>% 
  arrange(St.label) %>% 
  filter(!is.na(value)) %>% 
  mutate(St.label = substr(St.label, 4,6)) %>% 
  ggplot() +
  geom_point(aes(x=St.label, y=value, col=Distribution),
             size=2.5) +
  scale_color_manual(values = c("red", "blue", "green")) +
  scale_y_log10() +
  theme_minimal() +
  ylab("xmin") +
  theme(axis.text.x=element_text(angle=50, size=7, vjust=0.5)) +
  ggtitle("Diatoms, metaB, 20-180, SUR",
          subtitle = "xmins; ylog")
dev.off()
```


![xmins_station_metaB](C:/Users/Userszn/Google Drive/PhD/script/metaB_metaG_metaT_cfrall/outputs/Per_Station/Fits/metaB/metaB_xmins_per_station.pdf){width=100% height=600}

<br>

5. Plot xmins per richness

```{r eval=FALSE}
###xmins per richness
metab <- read.delim(file="C:/Users/Userszn/Google Drive/PhD/TARA_Data/metab/all_taxa/dia.txt",
                     sep = ",", stringsAsFactors = F) %>% 
  select(contains("_"), cid) %>%
  column_to_rownames("cid")

dat_samp <- read.delim("~/PhD/TARA_Data/dat_samp.txt") %>% 
  select(Sample.id, Depth, Fraction.size, Station.label,
         Latitude, Longitude, Temperature, Marine.biome, Ocean.region) %>% 
  filter(Depth == "SRF", Fraction.size == "20-180")


##filter metab
metab_richness <- metab[,names(metab)%in%dat_samp$Sample.id] %>%
  rownames_to_column("cid") %>%
  gather (Sample.id, values, -cid) %>% 
  merge(dat_samp) %>% 
  filter(values >0) %>% 
  group_by(Station.label) %>% 
  summarise(n_distinct(cid)) %>% 
  rename(St.label = Station.label) %>% 
  mutate(St.label = substr(St.label, 6, 8)) %>% 
  rename(richness = "n_distinct(cid)")
  


pdf("metaB_xmins_per_richness.pdf", width = 8.5)
as.data.frame(t(d)) %>%
  rename(exponential = xmin_exp,
         powerlaw = xmin_pl,
         lognormal = xmin_lno) %>% 
  rownames_to_column("St.label") %>% 
  gather(Distribution, value, -St.label) %>% 
  arrange(St.label) %>% 
  filter(!is.na(value)) %>% 
  mutate(St.label= substr(St.label, 4,6)) %>%
  inner_join(metab_richness) %>% 
  ggplot() +
  geom_point(aes(x=richness, y=value, col=Distribution),
             size=2.5) +
  scale_color_manual(values = c("red", "blue", "green")) +
  scale_y_log10() +
  scale_x_log10() +
  theme_minimal() +
  ylab("xmin") +
  #theme(axis.text.x=element_text(angle=50, size=7, vjust=0.5)) +
  ggtitle("Diatoms, metaB, 20-180, SUR",
          subtitle = "xmins; xylog") +
  facet_wrap(~Distribution, scales = "free")
dev.off()
```

![xmins_richness_metaB](C:/Users/Userszn/Google Drive/PhD/script/metaB_metaG_metaT_cfrall/outputs/Per_Station/Fits/metaB/metaB_xmins_per_richness.pdf){width=100% height=600}

<br>
<br>
<br>

6. Plot pars per station

```{r eval=FALSE}
############################ pars ############################
load("pars_all_stations_explno_vector500_metaB.RData")

##pars per station
pdf("metaB_pars_per_station.pdf", width = 8.5)
as.data.frame(t(d_pars)) %>% 
  na.omit(f) %>%  
  rownames_to_column("St.label") %>% 
  select(-c(pars_lno2)) %>% 
  mutate(pars_lno1 = abs(pars_lno1),
         St.label= substr(St.label, 4,6)) %>%
  mutate(St.label = sprintf("%03d", as.numeric(St.label))) %>%
  rename(exponential_lambda = pars_exp,
         lognormal_mu = pars_lno1,
         powerlaw_alpha = pars_pl) %>% 
  gather(Par, value, -St.label) %>% 
  arrange(St.label) %>% 
  filter(!is.na(value)) %>% 
  ggplot() +
  geom_point(aes(x=St.label, y=value, col=Par),
             size=2.5) +
  scale_color_manual(values = c("red", "blue", "green")) +
  scale_y_log10() +
  theme_minimal() +
  theme(axis.text.x=element_text(angle=50, size=7, vjust=0.5)) +
  ggtitle("Diatoms, metaB, 20-180, SUR",
          subtitle = "parameters; ylog")
dev.off()
```

![pars_station_metaB](C:/Users/Userszn/Google Drive/PhD/script/metaB_metaG_metaT_cfrall/outputs/Per_Station/Fits/metaB/metaB_pars_per_station.pdf){width=100% height=600}

<br>

7. Plot pars per richness

```{r eval=FALSE}
###pars per richness
pdf("metaB_pars_per_richness.pdf", width = 8.5)
as.data.frame(t(d_pars)) %>% 
  na.omit(f) %>%  
  rownames_to_column("St.label") %>% 
  select(-c(pars_lno2)) %>% 
  mutate(pars_lno1 = abs(pars_lno1),
         St.label= substr(St.label, 4,6)) %>%
  mutate(St.label = sprintf("%03d", as.numeric(St.label))) %>%
  rename(exponential_lambda = pars_exp,
         lognormal_mu = pars_lno1,
         powerlaw_alpha = pars_pl) %>% 
  gather(Par, value, -St.label) %>% 
  arrange(St.label) %>% 
  filter(!is.na(value)) %>% 
  inner_join(metab_richness) %>% 
  ggplot() +
  geom_point(aes(x=richness, y=value, col=Par),
             size=2.5) +
  scale_color_manual(values = c("red", "blue", "green")) +
  scale_y_log10() +
  scale_x_log10() +
  theme_minimal() +
  #theme(axis.text.x=element_text(angle=50, size=7, vjust=0.5)) +
  ggtitle("Diatoms, metaB, 20-180, SUR",
          subtitle = "parameters; xylog") +
  facet_wrap(~Par, scales = "free") 
dev.off()
```

![pars_richness_metaB](C:/Users/Userszn/Google Drive/PhD/script/metaB_metaG_metaT_cfrall/outputs/Per_Station/Fits/metaB/metaB_pars_per_richness.pdf){width=100% height=600}
